### 2018-05-04 Presentation/Presentation.tex
VN

\documentclass{beamer}
\usetheme[
  block=fill,
  background=dark,
  titleformat=smallcaps,
  progressbar=frametitle,
  numbering=none,
]{metropolis}

%----------------------------------------------------------------------------
% LoCo
%----------------------------------------------------------------------------
\setbeamertemplate{frametitle}[default][center]

%Color
\definecolor{mDarkBrown}{HTML}{604c38}
\definecolor{mDarkTeal}{HTML}{23373b}
\definecolor{mLightBrown}{HTML}{EB811B}
\definecolor{mLightGreen}{HTML}{14B03D}
% Math
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
% Code listing
\usepackage{minted}
%\usemintedstyle{friendly}
\usemintedstyle{tango}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

% Graphs
\usepackage{tikz}
\usetikzlibrary{calc, trees, fit}
\usepackage{pgfplots}
% Graphics
\usepackage{graphics}
\graphicspath{{figures/}} % Location of the graphics files

\newcommand\todo[1]{\textcolor{red}{#1}}
\newcommand{\w}[1]{\textit{"#1"}}
\newcommand{\sm}[1]{\text{\small{#1}}}
\newcommand\s{\textsc}

% Box macro
\newcommand{\ex}[2]{
  \vfill
  \begin{alertblock}{#1}
    #2
  \end{alertblock}
}
\newcommand\tsc[1]{\alert{\textsc{#1}}}

%----------------------------------------------------------------------------

% Beamer
\title{Differentiable Neural Computers}
\subtitle{Hybrid Computing using a neural network with dynamic external memory (Graves et al. 2016)}
\author{Konstantinos Kogkalidis}
\date{May 28, 2018}
\institute{Universiteit Utrecht}

\begin{document}
	\maketitle

\begin{frame}{Overview}
	A \alert{recurrent neural network} controlling a large external memory.

	\pause
	Key Features:
	\begin{itemize}
	\item End-to-end differentiable
	\item Turing complete
	\item Extension of NTMs
	\end{itemize}
\end{frame}

\begin{frame}{Introduction: Motivation}
	Von Neumann architecture
	\begin{figure}
	\begin{tikzpicture}
		[auto,
		block/.style ={rectangle, draw=mDarkBrown, thick, fill=gray!20, text width=5em, align=center, rounded corners, minimum height=2em},
		block2/.style ={rectangle, draw=mDarkBrown, thick, fill=mDarkTeal, text width=5em, align=center, rounded corners, minimum height=2em},
		block3/.style ={rectangle, draw=black, thick, fill=gray!20, text width=5em, align=center, rounded corners, minimum height=2em}]
		\draw (-1,0.63) node[block3] (i) {\textcolor{mDarkTeal}{\sc{input}}};
		\draw (6,0.63) node[block3] (o) {\textcolor{mDarkTeal}{\sc{output}}};

		\draw (2.5,-1) node[block2] (m) {\textcolor{gray!20}{\sc{memory}}};
		\draw (2.5,1) node[block] (a) {\textcolor{mDarkTeal}{\sc{alu}}};
		\draw (2.5,2) node[block] (c) {\textcolor{mDarkTeal}{\sc{control unit}}};

		\node[draw=mDarkBrown, thick, fill=mDarkBrown, fit=(a) (c)](Fit1) {};
		\draw (2.5,1) node[block] (a) {\textcolor{mDarkTeal}{\sc{alu}}};
		\draw (2.5,2) node[block] (c) {\textcolor{mDarkTeal}{\sc{control unit}}};

		\node[draw=black, thick, fill=gray!20, fit=(Fit1) (m)](Fit2) {};
		\node[draw=mDarkBrown, thick, fill=mDarkBrown, fit=(a) (c)](Fit1) {};
		\draw (2.5,1) node[block] (a) {\textcolor{mDarkTeal}{\sc{alu}}};
		\draw (2.5,2) node[block] (c) {\textcolor{mDarkTeal}{\sc{control unit}}};
		\draw (2.5,-1) node[block2] (m) {\textcolor{gray!20}{\sc{memory}}};

		\draw (i) edge [->, black, thick] (Fit2);
		\draw (Fit2) edge [->, black, thick] (o);
		\draw ($(m.north) + (0.25,0)$) edge [<-, mDarkBrown, thick] ($(Fit1.south) + (0.25, 0)$ );
		\draw ($(m.north) + (-0.25,0)$) edge [->, mDarkTeal, thick] ($(Fit1.south) + (-0.25, 0)$ );

	\end{tikzpicture}
	\end{figure}
\end{frame}

\end{document}

### 2018-05-04 Presentation/Presentation.tex
sNN, rNN prework

@@
 \begin{frame}{Introduction: Motivation}
-	Von Neumann architecture
+	\alert{Von Neumann architecture}
 	\begin{figure}
@@
 
+\begin{frame}{Introduction: Motivation}
+	\begin{minipage}{.4\textwidth}	
+	\alert{Simple Neural Net}
+	\begin{figure}
+	\begin{tikzpicture}[scale=.5]
+		\foreach \y /\alph/\name in {
+			0/x1/$x_1$,
+		  	-1/x2/$x_2$,
+		  	-2/x3/$x_3$,
+		  	-4/xM/$x_M$
+		 }{
+		% 	\node[] (\alph) at (0,\y) {\name};
+		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{mDarkTeal}{\name}};
+		 }
+		 \node (x..) at (0,-3) {\tiny {\vdots}};
+		 \foreach \y /\alph/\name in {
+			1/h1/$h_1$,
+		  	0/h2/$h_2$,
+		  	-1/h3/$h_3$,
+		  	-5/hN/$h_N$
+		 }{
+		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (4,\y) {\tiny \textcolor{mDarkTeal}{\name}};
+		 }
+		 \node (h..) at (4,-3) {\tiny {\vdots}};
+		 \foreach \y /\alph/\name in {
+			0/y1/$y_1$,
+		  	-1/y2/$y_2$,
+		  	-2/y3/$y_3$,
+		  	-4/yP/$y_P$
+		 }{
+		 	\node[circle, draw=gray!90,inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (8,\y) {\tiny \textcolor{mDarkTeal}{\name}};
+		 }
+		 \node (y..) at (8,-3) {\tiny {\vdots}};
+		 \foreach \x in {x1, x2, x3, xM}
+		 {\foreach \h in {h1, h2, h3, hN}
+		 {\draw (\x) edge[gray!90] (\h);}}
+		 \foreach \x in {h1, h2, h3, hN}
+		 {\foreach \y in {y1, y2, y3, yP}
+		 {\draw (\x) edge[gray!90] (\y);}}
+	\end{tikzpicture}
+	\end{figure}
+	\end{minipage}
+	\pause
+	\hspace{1cm}
+	\begin{minipage}{.4\textwidth}	
+	\alert{Recurrent Neural Net}
+	\begin{figure}
+	\begin{tikzpicture}[scale=.25]
+		\foreach \y /\alph/\name in {
+			0/x1/$x_1$,
+		  	-1/x2/$x_2$,
+		  	-2/x3/$x_3$,
+		  	-4/xM/$x_M$
+		 }{
+		% 	\node[] (\alph) at (0,\y) {\name};
+		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{mDarkTeal}{\name}};
+		 }
+		 \node (x..) at (0,-3) {\tiny {\vdots}};
+		 \foreach \y /\alph/\name in {
+			1/h1/$h_1$,
+		  	0/h2/$h_2$,
+		  	-1/h3/$h_3$,
+		  	-5/hN/$h_N$
+		 }{
+		 	\node[circle, draw=gray!90, thick, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (4,\y) {\tiny \textcolor{mDarkTeal}{\name}};
+		 }
+		 \node (h..) at (4,-3) {\tiny {\vdots}};
+		 \foreach \y /\alph/\name in {
+			0/y1/$y_1$,
+		  	-1/y2/$y_2$,
+		  	-2/y3/$y_3$,
+		  	-4/yP/$y_P$
+		 }{
+		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (8,\y) {\tiny \textcolor{mDarkTeal}{\name}};
+		 }
+		 \node (y..) at (8,-3) {\tiny {\vdots}};
+		 \foreach \x in {x1, x2, x3, xM}
+		 {\foreach \h in {h1, h2, h3, hN}
+		 {\draw (\x) edge[dotted, gray!90] (\h);}}
+		 \foreach \x in {h1, h2, h3, hN}
+		 {\foreach \y in {y1, y2, y3, yP}
+		 {\draw (\x) edge[dotted, gray!90] (\y);}}
+		 \foreach \h in {h1}
+		 {\draw (\h.west) [<-, red] .. controls +(-0.8,0.8) and +(0.8,0.8) .. (\h.east);}
+		 \foreach \h in {h1}
+		 {\foreach \hh in {h2, h3, hN}
+		 {\draw (\h.east) edge[->, red] (\hh.west);}}
+	\end{tikzpicture}
+	\end{figure}
+	\end{minipage}
+\end{frame}
+
 \end{document}

### 2018-05-04 Presentation/Presentation.tex
memory referencing

@@
 \usepackage{stmaryrd}
+\usepackage{bm}
 % Code listing
@@
 \date{May 28, 2018}
-\institute{Universiteit Utrecht}
+\institute{Logic and Computation}
 
@@
 \begin{frame}{Overview}
-	A \alert{recurrent neural network} controlling a large external memory.
+	\alert{Differentiable Neural Computer}\\
+	A recurrent neural network coupled with an external memory.
 
 	\pause
-	Key Features:
 	\begin{itemize}
+	\item Extension of NTMs
+	\begin{itemize}
+		\pause
 		\item End-to-end differentiable
+		\pause
+		\item Auto-associative memory
+		\pause
 		\item Turing complete
-	\item Extension of NTMs
+		\pause
+		\item[+] Memory attention mechanisms
+		\end{itemize}
+	\pause
+	\item Mimic mammalian biological memory
+	\item Employ classical concepts of computation
 	\end{itemize}
@@
 \begin{frame}{Introduction: Motivation}
-	\begin{minipage}{.4\textwidth}	
+	\begin{minipage}[t]{.44\textwidth}	
 	\alert{Simple Neural Net}
-	\begin{figure}
+	\begin{figure}[h!]
+	\vspace{6.5pt}
 	\begin{tikzpicture}[scale=.5]
@@
 		 }{
-		% 	\node[] (\alph) at (0,\y) {\name};
 		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{mDarkTeal}{\name}};
@@
 	\end{figure}
+	\vspace{10pt}
+	\centering
+	\small \alert{$y=g(h),\ h=f(x)$}\\
+	No memory
 	\end{minipage}
@@
 	\hspace{1cm}
-	\begin{minipage}{.4\textwidth}	
+	\begin{minipage}[t]{.44\textwidth}	
 	\alert{Recurrent Neural Net}
-	\begin{figure}
-	\begin{tikzpicture}[scale=.25]
+	\begin{figure}[h!]
+	\begin{tikzpicture}[scale=.5]
 		\foreach \y /\alph/\name in {
@@
 		 }{
-		 	\node[circle, draw=gray!90, thick, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (4,\y) {\tiny \textcolor{mDarkTeal}{\name}};
+		 	\node[circle, draw=mLightBrown, inner sep=0pt,minimum size=3mm,fill=gray!20] (\alph) at (4,\y) {\tiny \textcolor{mDarkTeal}{\name}};
 		 }
@@
 		 {\foreach \h in {h1, h2, h3, hN}
-		 {\draw (\x) edge[dotted, gray!90] (\h);}}
+		 {\draw (\x) edge[gray!90] (\h);}}
 		 \foreach \x in {h1, h2, h3, hN}
 		 {\foreach \y in {y1, y2, y3, yP}
-		 {\draw (\x) edge[dotted, gray!90] (\y);}}
-		 \foreach \h in {h1}
-		 {\draw (\h.west) [<-, red] .. controls +(-0.8,0.8) and +(0.8,0.8) .. (\h.east);}
-		 \foreach \h in {h1}
-		 {\foreach \hh in {h2, h3, hN}
-		 {\draw (\h.east) edge[->, red] (\hh.west);}}
+		 {\draw (\x) edge[gray!90] (\y);}}
+		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(0.8,0.8) and +(-0.8,0.8) .. (h1.west);
+		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(0.4,-0.8) and +(-0.4,0.8) .. (h2.west);
+		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(1,-1.6) and +(-0.6,0.4) .. (h3.west);
+		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(2,-2) and +(-2,2) .. (hN.west);
 	\end{tikzpicture}
 	\end{figure}
+	\vspace{10pt}
+	\centering
+	\small{ \alert{$h(t)=f([x(t); h(t-1)])$}}\\
+	Finite, non-contiguous memory
 	\end{minipage}
@@
 
+\begin{frame}{Approach}
+	Allow an RNN to act as a controller to interact with a memory matrix of N (arbitrary many) addresses.
+	\pause
+	\begin{enumerate}
+	\item \alert{Content Lookup}\\
+		\begin{itemize}
+		\item \alert{Attention} over memory defined by weightings $W \in \mathbb{R}^N$
+		\item Compare controller output with memory objects (\alert{auto-associative memory})
+		\item Allow partial matches  (\alert{pattern completion})
+		\end{itemize}
+	\pause
+	\item \alert{Sequential Retrieval}
+		\begin{itemize} 
+		\item Fill $L \in \{0,1\}^{2N}$ indexing \alert{temporal transitions}
+		\item \alert{Shift} operations defined by $LW,\ L^TW$
+		\end{itemize}
+	\pause
+	\item \alert{Dynamic Allocation}
+		\begin{itemize}
+		\item Mark memory locations with $\{0,1\}$ to \alert{signal usage}
+		\item Manipulate signals during R/W operations to enable \alert{reallocation}
+		\item Generalization to \alert{unbounded memory}
+		\end{itemize}
+	\end{enumerate}
+\end{frame}
+
+\begin{frame}{Controller}
+A deep long-short term memory unit receiving 
+\[
+\pmb{\small{\mathcal{X}}}_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots \pmb{r}_{t-1}^R]
+\]
+and producing
+\[
+\pmb{a}
+\]
+\end{frame}
 \end{document}

### 2018-05-04 Presentation/Presentation.tex
LSTM sketch

@@
 \setbeamertemplate{frametitle}[default][center]
+\newcommand{\xx}{\pmb{\raisebox{-1.5pt}{$\mathcal{X}$}}}
+\newcommand{\hh}{\pmb{h}}
+\newcommand{\ii}{\pmb{i}}
+\newcommand{\oo}{\pmb{o}}
+\newcommand{\ff}{\pmb{f}}
+\newcommand{\Ss}{\pmb{s}}
+\newcommand{\bb}{\pmb{b}}
 
@@
 \usepackage{tikz}
-\usetikzlibrary{calc, trees, fit}
+\usetikzlibrary{calc, trees, fit, positioning}
 \usepackage{pgfplots}
@@
 \newcommand{\sm}[1]{\text{\small{#1}}}
-\newcommand\s{\textsc}
 
@@
 \begin{frame}{Approach}
-	Allow an RNN to act as a controller to interact with a memory matrix of N (arbitrary many) addresses.
+	Train a RNN to act as a \alert{controller} to interact with a memory matrix of N (arbitrary many) addresses.
 	\pause
@@
 \begin{frame}{Controller}
-A deep long-short term memory unit receiving 
+	A deep \alert{long short-term memory network} receiving 
 	\[
-\pmb{\small{\mathcal{X}}}_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots \pmb{r}_{t-1}^R]
+	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots \pmb{r}_{t-1}^R]
 	\]
@@
 	\[
-\pmb{a}
+	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\theta)
 	\]
+	where $\mathcal{N}$ a set of state equations and $\theta$ their trainable parameters.
+\end{frame}
+
+\begin{frame}{Controller}
+	A more detailed look into $\mathcal{N}$ and LSTMs:\\
+	\begin{align}
+	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
+	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
+	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
+	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
+	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
+	\nonumber \\ 
+	\pmb{v}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
+	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
+	\end{align}
+\end{frame}
+
+\begin{frame}{Controller}
+	\begin{figure}
+	\begin{tikzpicture}[scale=0.5]
+		% LSTM
+		% outer box
+		\draw[thick] (0,0) |- (18,12);
+		\draw[thick] (18,12) |- (0,0);
+		% core nodes
+		\node (s) at (9,6) {$s$};
+		\node (fx) at (9,4) {$x$};
+		\node (f) at (9,2) {$f$};
+		\node (i) at (6,8) {$i$};
+		\node (ix) at (6,6) {$x$};
+		\node (id) at (4,6) {$S$};
+		\node (o) at (12,10) {$o$};
+		\node (ox) at (16,6) {$x$};
+		\node (od) at (12,6) {$S$};
+		% recurrency
+		\draw (f) -| (2,6);
+		\draw (2,6) |- (o);
+		% gates
+		\draw (o) edge (ox);
+		\draw (i) edge (ix);
+		\draw (s) edge[bend right=90] (fx);
+		\draw (s) edge[bend left=90] (fx);
+		\draw (f) edge (fx);
+		% forward
+		\draw (0,6) edge (9,6);
+		\draw (s) edge (od);
+		\draw (od) edge (18,6);
+		\end{tikzpicture}
+	\end{figure}
 \end{frame}

### 2018-05-04 Presentation/Presentation.tex
LSTM slide

@@
 	\[
-	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots \pmb{r}_{t-1}^R]
+	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots ;\pmb{r}_{t-1}^R]
 	\]
@@
 \begin{frame}{Controller}
+	\alert{Single LSTM Layer}
 	\begin{figure}
 	\begin{tikzpicture}[scale=0.5]
+		%-------------------------------------------------------------------------------
 		% LSTM
+		%-------------------------------------------------------------------------------
+		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
+			at (-0,6) {\textcolor{mDarkTeal}{$;$}};
+
 		% outer box
-		\draw[thick] (0,0) |- (18,12);
-		\draw[thick] (18,12) |- (0,0);
+		\draw[densely dotted, thick, gray!90] (18,6) -| (18,12);
+		\draw[densely dotted, thick,->, gray!90] (18,12) -| (conc);
+		%\draw[thick] (0,0) |- (18,12);
+		%\draw[thick] (18,12) |- (0,0);
+
 		% core nodes
-		\node (s) at (9,6) {$s$};
-		\node (fx) at (9,4) {$x$};
-		\node (f) at (9,2) {$f$};
-		\node (i) at (6,8) {$i$};
-		\node (ix) at (6,6) {$x$};
-		\node (id) at (4,6) {$S$};
-		\node (o) at (12,10) {$o$};
-		\node (ox) at (16,6) {$x$};
-		\node (od) at (12,6) {$S$};
+		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
+			at (-0,6) {\textcolor{mDarkTeal}{$;$}};
+		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (s) 
+			at (9,6) {\large\textcolor{black}{$\Ss_t$}};
+		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (fx) 
+			at (9,4) {\textcolor{mDarkTeal}{$\times$}};
+		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (f) 
+			at (9,2) {\large\textcolor{black}{$\ff_t$}};
+		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (i) 
+			at (6,8) {\large\textcolor{black}{$\ii_t$}};
+		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (ix) 
+			at (6,6) {\textcolor{mDarkTeal}{$\times$}};
+		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (id) 
+			at (4,8) {\textcolor{mDarkTeal}{$\int$}};
+		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (sd) 
+			at  (4,6) {\small\textcolor{mDarkTeal}{$\int$}};
+		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (o) 
+			at (12,10) {\large\textcolor{black}{$\oo_t$}};
+		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (ox) 
+			at (16,6) {\textcolor{mDarkTeal}{$\times$}};
+		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (od) 
+			at (12,6) {\small\textcolor{mDarkTeal}{$\int$}};
+		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (odd) 
+			at (4,10) {\small\textcolor{mDarkTeal}{$\int$}};
+		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (fd) 
+			at (4,2) {\small\textcolor{mDarkTeal}{$\int$}};
 		% recurrency
-		\draw (f) -| (2,6);
-		\draw (2,6) |- (o);
+		\draw (f) edge[thick] (fd);
+		\draw[thick] (fd) -| (2,6);
+		\draw[thick] (2,6) |- (odd);
+		\draw (odd) edge[->,thick] (o);
+		\draw[thick] (2,6) |- (id);
+		\draw (id) edge[thick] (i);
 		% gates
-		\draw (o) edge (ox);
-		\draw (i) edge (ix);
-		\draw (s) edge[bend right=90] (fx);
-		\draw (s) edge[bend left=90] (fx);
-		\draw (f) edge (fx);
+		\draw (o) edge[->, thick] (ox);
+		\draw (i) edge[->, thick] (ix);
+		\draw (s) edge[->,bend right=45, thick, densely dotted, gray!90] (fx);
+		\draw (s) edge[<-,bend left=45, thick] (fx);
+		\draw (f) edge[->, thick] (fx);
 		% forward
-		\draw (0,6) edge (9,6);
-		\draw (s) edge (od);
-		\draw (od) edge (18,6);
+		\draw(-2,6) edge[thick] (conc);
+		\draw (0,6) edge[thick] (sd);
+		\draw (sd) edge[->, thick] (ix);
+		\draw (ix) edge[->, thick] (s);
+		\draw (s) edge[thick] (od);
+		\draw (od) edge[->, thick] (ox);
+		\draw (ox) edge[->, thick] (20,6);
+
+		% labels
+		\node[label=above:$\textcolor{white}{\xx_t}$] (x) at (-1,6) {};
+		\node[label=above:$\textcolor{white}{\hh_t}$] (ht) at (19.5,6) {};
+		\node[label=above:$\textcolor{white}{\hh_{t-1}}$] (x) at (9,12) {};
 		\end{tikzpicture}

### 2018-05-05 Presentation/Presentation.tex
through-time connections

@@
 \begin{frame}{Controller}
-	A deep \alert{long short-term memory network} receiving 
+	A deep \alert{long short-term memory network} receiving input:
 	\[
@@
 	\]
-	and producing 
+	and producing output:
 	\[
-	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\theta)
+	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
 	\]
-	where $\mathcal{N}$ a set of state equations and $\theta$ their trainable parameters.
+	where $\mathcal{N}$ a set of state equations and $\vartheta$ their trainable parameters.
 \end{frame}
 
-\begin{frame}{Controller}
-	A more detailed look into $\mathcal{N}$ and LSTMs:\\
+\begin{frame}{Controller: State Equations}
+	A more detailed look into $\mathcal{N}$:\\
 	\begin{align}
@@
 
-\begin{frame}{Controller}
-	\alert{Single LSTM Layer}
+\begin{frame}{Controller: Signal-Flow}
+	\alert{Single LSTM layer}
 	\begin{figure}
@@
 		% core nodes
-		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
-			at (-0,6) {\textcolor{mDarkTeal}{$;$}};
+		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
+			at (-0,6) {\textcolor{black}{$;$}};
 		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (s) 
-			at (9,6) {\large\textcolor{black}{$\Ss_t$}};
-		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (fx) 
-			at (9,4) {\textcolor{mDarkTeal}{$\times$}};
+			at (9,6) {\large\textcolor{black}{$\Ss_t^l$}};
+		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (fx) 
+			at (9,4) {\textcolor{black}{$\times$}};
 		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (f) 
-			at (9,2) {\large\textcolor{black}{$\ff_t$}};
+			at (9,2) {\large\textcolor{black}{$\ff_t^l$}};
 		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (i) 
-			at (6,8) {\large\textcolor{black}{$\ii_t$}};
-		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (ix) 
-			at (6,6) {\textcolor{mDarkTeal}{$\times$}};
-		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (id) 
-			at (4,8) {\textcolor{mDarkTeal}{$\int$}};
-		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (sd) 
-			at  (4,6) {\small\textcolor{mDarkTeal}{$\int$}};
+			at (6,8) {\large\textcolor{black}{$\ii_t^l$}};
+		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (ix) 
+			at (6,6) {\textcolor{black}{$\times$}};
+		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (id) 
+			at (4,8) {\textcolor{black}{$\int$}};
+		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (sd) 
+			at  (4,6) {\small\textcolor{black}{$\int$}};
 		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (o) 
-			at (12,10) {\large\textcolor{black}{$\oo_t$}};
-		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (ox) 
-			at (16,6) {\textcolor{mDarkTeal}{$\times$}};
-		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (od) 
-			at (12,6) {\small\textcolor{mDarkTeal}{$\int$}};
-		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (odd) 
-			at (4,10) {\small\textcolor{mDarkTeal}{$\int$}};
-		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (fd) 
-			at (4,2) {\small\textcolor{mDarkTeal}{$\int$}};
+			at (12,10) {\large\textcolor{black}{$\oo_t^l$}};
+		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (ox) 
+			at (16,6) {\textcolor{black}{$\times$}};
+		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (od) 
+			at (12,6) {\small\textcolor{black}{$\int$}};
+		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (odd) 
+			at (4,10) {\small\textcolor{black}{$\int$}};
+		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (fd) 
+			at (4,2) {\small\textcolor{black}{$\int$}};
 		% recurrency
@@
 		% forward
-		\draw(-2,6) edge[thick] (conc);
+		\draw (-2,4)[->,thick] -| (conc);
+		\draw(-2,6) edge[thick,->] (conc);
 		\draw (0,6) edge[thick] (sd);
@@
 		% labels
+		\node[label=below:$\textcolor{white}{\hh_t^{l-1}}$] (ht1) at (-1,4) {};
 		\node[label=above:$\textcolor{white}{\xx_t}$] (x) at (-1,6) {};
-		\node[label=above:$\textcolor{white}{\hh_t}$] (ht) at (19.5,6) {};
-		\node[label=above:$\textcolor{white}{\hh_{t-1}}$] (x) at (9,12) {};
+		\node[label=above:$\textcolor{white}{\hh_t^l}$] (ht) at (19.5,6) {};
+		\node[label=above:$\textcolor{white}{\hh_{t-1}^l}$] (x) at (9,12) {};
 		\end{tikzpicture}

### 2018-05-05 Presentation/Presentation.tex
Probprog

@@
 	\maketitle
+
+\begin{frame}{Probabilistic Programming}
+	Cross-domain
+	\begin{itemize}
+	\item Data Flow Programming
+	\item Bayesian Reasoning
+	\item Machine Learning
+	\item Functional Programming
+	\end{itemize}
+	\pause
+	Intuition:
+	\textit{"Rather than explicitly write a program, write some \alert{constraints} on the behavior of the desired program and use computational tools to search the program space for \alert{models} satisfying these constraints."}
+	\pause
+	\[\begin{array}{rl}
+	\textsc{Program} & \textsc{Model}\\
+	\hline
+	Discrete & Continuous\\
+	Deterministic & Stochastic\\
+	Static & Adaptive\\
+	\end{array}\]
+\end{frame}
 
@@
 	\begin{minipage}[t]{.44\textwidth}	
-	\alert{Recurrent Neural Net}
+	\alert{Simple Recurrent Net}
 	\begin{figure}[h!]
@@
 	\end{minipage}
+	\pause
+
+	\begin{quote}
+	\small \textit{"If training vanilla neural nets is optimization over functions, training recurrent nets is \alert{optimization over programs.}"}
+	\end{quote}
+\end{frame}
+
+\begin{frame}{Introduction: Motivation}
+
 \end{frame}
@@
 		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (o) 
-			at (12,10) {\large\textcolor{black}{$\oo_t^l$}};
+			at (16,10) {\large\textcolor{black}{$\oo_t^l$}};
 		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (ox) 
@@
 \end{frame}
+
+\begin{frame}{Controller: Outputs}
+	\topskip0pt
+	\vspace*{\fill}
+	\[
+	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
+	\]
+	\pause
+	Output given by:
+	\[
+	\pmb{y}_t = \pmb{v}_t + W_R[\pmb{r}_t^1;\dots;\pmb{r}_t^R] \tag{hello}
+	\]
+\end{frame}
+
+\begin{frame}{Controller: Outputs}
+	\topskip0pt
+	\[
+	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
+	\]
+	\vspace{5pt}
+	\pause
+	\begin{equation*}
+	\begin{split}
+	\pmb\xi_t = [ \pmb{k}_t^{r,1};\dots;\pmb{k}_t^{r,R};\ 
+				\hat{\beta}_t^{r,1};\dots;\hat{\beta}_t^{r,R};\ 
+				\pmb{k}_t^w;\ \hat{\beta}_t^w; \\
+				\hat{\pmb{e}}_t;\
+				\pmb{v}_t;\ \hat{\pmb{f}}_t^1;\dots;\hat{\pmb{f}_t^R};\ 
+				\hat{g}_t^a;\ \hat{g}_t^w;\ \hat{\pmb{\pi}}_t^1;\dots;\hat{\pmb{\pi}}_t^R;]					
+	\end{split}
+	\end{equation*}
+\end{frame}
+
+\begin{frame}{Controller: Outputs}
+	\topskip0pt
+	\[
+	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
+	\]
+	\vspace{5pt}
+	\begin{equation*}
+	\begin{split}
+	\pmb\xi_t = [\overbrace{\pmb{k}_t^{r,1};\dots;\pmb{k}_t^{r,R};\ }^\text{\alert{R read keys}}
+				\hat{\beta}_t^{r,1};\dots;\hat{\beta}_t^{r,R};\ 
+				\pmb{k}_t^w;\ \hat{\beta}_t^w; \\
+				\hat{\pmb{e}}_t;\
+				\pmb{v}_t;\ \hat{\pmb{f}}_t^1;\dots;\hat{\pmb{f}_t^R};\ 
+				\hat{g}_t^a;\ \hat{g}_t^w;\ \hat{\pmb{\pi}}_t^1;\dots;\hat{\pmb{\pi}}_t^R;]					
+	\end{split}
+	\end{equation*}
+
+\end{frame}
+
 \end{document}

### 2018-05-05 Presentation/Presentation.tex
Further reading

@@
 
-\begin{frame}{Probabilistic Programming}
-	Cross-domain
+\begin{frame}{Overview: Probabilistic Programming}
+	\alert{Cross-domain}
 	\begin{itemize}
@@
 	\pause
-	\[\begin{array}{rl}
-	\textsc{Program} & \textsc{Model}\\
+	\[\begin{array}{rcl}
+	\textsc{\alert{Program}} &\ & \textsc{\alert{Model}}\\
 	\hline
-	Discrete & Continuous\\
-	Deterministic & Stochastic\\
-	Static & Adaptive\\
+	\text{Discrete} &\ & \text{Continuous}\\
+	\text{Deterministic} &\ & \text{Stochastic}\\
+	\text{Static} &\ & \text{Adaptive}\\
 	\end{array}\]
@@
 
-\begin{frame}{Overview}
+\begin{frame}{Overview: DNC}
 	\alert{Differentiable Neural Computer}\\
@@
 
-\begin{frame}{Introduction: Motivation}
+\begin{frame}{Introduction: Classic Computation}
 	\alert{Von Neumann architecture}
@@
 
-\begin{frame}{Introduction: Motivation}
+\begin{frame}{Introduction: RNNs}
 	\begin{minipage}[t]{.44\textwidth}	
@@
 	\begin{split}
-	\pmb\xi_t = [\overbrace{\pmb{k}_t^{r,1};\dots;\pmb{k}_t^{r,R};\ }^\text{\alert{R read keys}}
-				\hat{\beta}_t^{r,1};\dots;\hat{\beta}_t^{r,R};\ 
-				\pmb{k}_t^w;\ \hat{\beta}_t^w; \\
-				\hat{\pmb{e}}_t;\
-				\pmb{v}_t;\ \hat{\pmb{f}}_t^1;\dots;\hat{\pmb{f}_t^R};\ 
-				\hat{g}_t^a;\ \hat{g}_t^w;\ \hat{\pmb{\pi}}_t^1;\dots;\hat{\pmb{\pi}}_t^R;]					
+	\pmb\xi_t = &[\overbrace{\pmb{k}_t^{r,1};\dots;\pmb{k}_t^{r,R};}^\text{\tiny\alert{read keys}}\
+				\overbrace{\hat{\beta}_t^{r,1};\dots;\hat{\beta}_t^{r,R};}^\text{\tiny\alert{read strengths}}\
+				\overbrace{\pmb{k}_t^w;\ \hat{\beta}_t^w;}^\text{\tiny\alert{write key/strength}} \
+				\overbrace{\hat{\pmb{e}}_t;}_\text{\tiny\alert{erase vector}} \\
+				&\underbrace{\pmb{v}_t;}_\text{\tiny\alert{write vector}} \
+				\underbrace{\hat{\pmb{f}}_t^1;\dots;\hat{\pmb{f}_t^R};}_\text{\tiny\alert{free gates}} \
+				\underbrace{\hat{g}_t^a;\ \hat{g}_t^w;}_\text{\tiny\alert{allocation/write gates}}\
+				\underbrace{\hat{\pmb{\pi}}_t^1;\dots;\hat{\pmb{\pi}}_t^R;}_\text{\tiny\alert{read modes}}]
 	\end{split}
 	\end{equation*}
+\end{frame}
 
+\begin{frame}{Further Reading}
+	\begin{itemize}
+	\item \alert{Neural Turing Machines} (Graves, Wayne, Danihelka)
+	\item \alert{Entity Networks} (Henaff, Weston, Szlam, Bordes, LeCun)
+	\item \alert{Principles of Probabilistic Programming Languages} (Goodman)
+	\item \alert{Backprop as a Functor} (Fong, Spivak, Tuyéras)
+	\item \alert{Formal Methods for Probabilistic Programming} (Selsam, Liang, Dill)
+	\end{itemize}
 \end{frame}

### 2018-05-05 Presentation/Presentation.tex
deep LSTM sketch

@@
 
-\begin{frame}{Introduction: Motivation}
-
-\end{frame}
-
 \begin{frame}{Approach}
-	Train a RNN to act as a \alert{controller} to interact with a memory matrix of N (arbitrary many) addresses.
+	Train a RNN to act as a \alert{controller} to interact with a memory matrix M of N (arbitrary many) addresses.
 	\pause
@@
 	\[
-	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
+	(\pmb{\upsilon}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
 	\]
@@
 	\nonumber \\ 
-	\pmb{v}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
+	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
 	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
@@
 
-\begin{frame}{Controller: Outputs}
-	\topskip0pt
-	\vspace*{\fill}
-	\[
-	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
-	\]
-	\pause
-	Output given by:
-	\[
-	\pmb{y}_t = \pmb{v}_t + W_R[\pmb{r}_t^1;\dots;\pmb{r}_t^R] \tag{hello}
-	\]
+\begin{frame}{Controller: Full View}
+	\alert{LSTM Network} (multiple layers)
+	\begin{figure}
+	\begin{tikzpicture}[scale=1]
+	\tikzset{miniLSTM/.style={draw=black, fill=white, minimum width=20pt, minimum height=10pt, thick}}
+	\tikzset{split/.style={circle, draw=black,inner sep=0pt, minimum size = 3mm, fill=white}}
+		\node (dummy_node) at (0,0) {};
+		\foreach \name/\x in {x1/2, x2/4, x3/6, xd/8, xL/10} {\node[inner sep=0] (\name) at (\x,0) {};}
+		\foreach \name/\x in {h1/3, h2/5, h3/7, hL/10} {\node[inner sep=0] (\name) at (\x, -2) {};}
+		\foreach \name/\x in {s0/3, s1/5, s2/7, sL/10} {\node[split] (\name) at (\x,-3) {$\textcolor{black}{\tiny;}$};}
+		\foreach \name/\x/\tag in {L1/2/$LSTM_1$, L2/4/$LSTM_2$, L3/6/$LSTM_3$, LL/10/$LSTM_L$} 
+		{\node[miniLSTM] (\name) at (\x,-2) {\textcolor{black}{\tiny\tag}};}
+		\node (Ld) at (8,-2) {$\dots$};
+		\node (sd) at (8,-3) {$\dots$};
+		\draw (dummy_node) -| (LL);
+		\draw (L1) edge[->] (L2);
+		\draw (L2) edge[->] (L3);
+		\draw (L3) edge[->] (Ld);
+		\draw (Ld) edge[->] (LL);
+		\draw[->] (x1) edge (L1.north);
+		\draw[->] (x2) edge (L2.north);
+		\draw[->] (x3) edge (L3.north);
+		\draw[->] (xL) edge (LL.north);
+		\draw[->] (xd) edge (Ld.north);
+		\draw[->] (1,0) |- (s0);
+		\draw[->] (h1) edge (s0);
+		\draw[->] (s0) edge (s1);
+		\draw[->] (h2) edge (s1);
+		\draw[->] (h3) edge (s2);
+		\draw[->] (s1) edge (s2);
+		\draw[->] (s2) edge (sd);
+		\draw[->] (sd) edge (sL);
+		\draw[->] (LL) edge (sL);		
+		\draw[->] (sL) edge (10, -5);
+		% labels
+		\node[label=above right :$\scriptsize\textcolor{white}{\xx_t}$] (xt) at (0,0) {};
+		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^1}$] (xt) at (3,-2) {};
+		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^2}$] (xt) at (5,-2) {};
+		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^3}$] (xt) at (7,-2) {};
+		\node[label=below :$\scriptsize\textcolor{white}{[\xx_t;\hh_t^1]}$] (xt) at (4,-3) {};
+		\node[label=below :$\scriptsize\textcolor{white}{[\xx_t;\hh_t^1;\hh_t^2]}$] (xt) at (6,-3) {};
+		\node[label=left :$\scriptsize\textcolor{white}{[\xx_t;\hh_t^1;\dots;\hh_t^L]}$] (xt) at (10,-5) {};
+	\end{tikzpicture}
+	\end{figure}
 \end{frame}
@@
 	\[
-	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
+	(\pmb{\upsilon}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
 	\]
 	\vspace{5pt}
+
 	\pause
-	\begin{equation*}
-	\begin{split}
-	\pmb\xi_t = [ \pmb{k}_t^{r,1};\dots;\pmb{k}_t^{r,R};\ 
-				\hat{\beta}_t^{r,1};\dots;\hat{\beta}_t^{r,R};\ 
-				\pmb{k}_t^w;\ \hat{\beta}_t^w; \\
-				\hat{\pmb{e}}_t;\
-				\pmb{v}_t;\ \hat{\pmb{f}}_t^1;\dots;\hat{\pmb{f}_t^R};\ 
-				\hat{g}_t^a;\ \hat{g}_t^w;\ \hat{\pmb{\pi}}_t^1;\dots;\hat{\pmb{\pi}}_t^R;]					
-	\end{split}
-	\end{equation*}
+	\alert{Intermediate output} $\pmb{\upsilon}_t$
+	\[
+	\pmb{y}_t = \pmb{\upsilon}_t + W_R[\pmb{r}_t^1;\dots;\pmb{r}_t^R] \tag{\alert{Memory-conditioning}}
+	\]
+
+	\pause
+	\alert{Interface vector} $\pmb\xi_t$
+
+	\begin{minipage}{0.49\textwidth}
+	\begin{itemize}
+		\item Read keys %$\pmb{k}_t^{r,i} \in \mathbb{R}^W$
+		\item Read strengths %$\beta_t^{r,i} \in [1,\infty)$
+		\item Write key %$\pmb{k}_t^w \in \mathbb{R}^W$	
+		\item Write strength %$\beta_t^{w} \in [1,\infty)$
+		\item Erase vector %$\pmb{e}_t \in [0,1]^W$	
+	\end{itemize}
+	\end{minipage}
+	\begin{minipage}{0.49\textwidth}
+	\begin{itemize}
+		\item Write vector %$\pmb{v}_t \in \mathbb{R}^W$
+		\item Free gates %$\pmb{f}_t^i \in [0,1]$		
+		\item Allocation gate %$g_t^a \in [0,1]$
+		\item Write gate %$g_t^w \in [0,1]$
+		\item Read modes %$\pmb{\pi}_t^i \in \mathcal{S}_3$
+	\end{itemize}
+	\end{minipage}
+%	\begin{equation*}
+%	\begin{split}
+%	\pmb\xi_t = &[\overbrace{\pmb{k}_t^{r,1};\dots;\pmb{k}_t^{r,R};}^\text{\tiny\alert{read keys}}\
+%				\overbrace{\hat{\beta}_t^{r,1};\dots;\hat{\beta}_t^{r,R};}^\text{\tiny\alert{read strengths}}\
+%				\overbrace{\pmb{k}_t^w;\ \hat{\beta}_t^w;}^\text{\tiny\alert{write key/strength}} \
+%				\overbrace{\hat{\pmb{e}}_t;}^\text{\tiny\alert{erase vector}} \\
+%				&\underbrace{\pmb{v}_t;}_\text{\tiny\alert{write vector}} \
+%				\underbrace{\hat{\pmb{f}}_t^1;\dots;\hat{\pmb{f}_t^R};}_\text{\tiny\alert{free gates}} \
+%				\underbrace{\hat{g}_t^a;\ \hat{g}_t^w;}_\text{\tiny\alert{allocation/write gates}}\
+%				\underbrace{\hat{\pmb{\pi}}_t^1;\dots;\hat{\pmb{\pi}}_t^R}_\text{\tiny\alert{read modes}}]
+%	\end{split}
+%	\end{equation*}
 \end{frame}
 
-\begin{frame}{Controller: Outputs}
-	\topskip0pt
+\begin{frame}{Memory Adressing: RW}
+\alert{Read operations}
 \[
-	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
+\pmb{r}_t^i = M_t^T\pmb{w}_t^{r,i}
 \]
-	\vspace{5pt}
-	\begin{equation*}
-	\begin{split}
-	\pmb\xi_t = &[\overbrace{\pmb{k}_t^{r,1};\dots;\pmb{k}_t^{r,R};}^\text{\tiny\alert{read keys}}\
-				\overbrace{\hat{\beta}_t^{r,1};\dots;\hat{\beta}_t^{r,R};}^\text{\tiny\alert{read strengths}}\
-				\overbrace{\pmb{k}_t^w;\ \hat{\beta}_t^w;}^\text{\tiny\alert{write key/strength}} \
-				\overbrace{\hat{\pmb{e}}_t;}_\text{\tiny\alert{erase vector}} \\
-				&\underbrace{\pmb{v}_t;}_\text{\tiny\alert{write vector}} \
-				\underbrace{\hat{\pmb{f}}_t^1;\dots;\hat{\pmb{f}_t^R};}_\text{\tiny\alert{free gates}} \
-				\underbrace{\hat{g}_t^a;\ \hat{g}_t^w;}_\text{\tiny\alert{allocation/write gates}}\
-				\underbrace{\hat{\pmb{\pi}}_t^1;\dots;\hat{\pmb{\pi}}_t^R;}_\text{\tiny\alert{read modes}}]
-	\end{split}
-	\end{equation*}
+\pause
+\alert{Write operations}
+\[
+M_t = M_{t-1} \circ (\pmb{1} - \pmb{w}_t^T\pmb{e}_t^T) + \pmb{w}_t^W\pmb{v}_t^T
+\]
 \end{frame}

### 2018-05-06 Presentation/Presentation.tex
minor fixes

@@
 	\centering
-	\small \alert{$y=g(h),\ h=f(x)$}\\
-	No memory
+	%\small \alert{$y=g(h),\ h=f(x)$}\\
+	\small $NN: \pmb{x}_{t_i} \mapsto \pmb{y}_{t_i}$\\
+	\alert{No memory}
 	\end{minipage}
@@
 	\centering
-	\small{ \alert{$h(t)=f([x(t); h(t-1)])$}}\\
-	Finite, non-contiguous memory
+	%\small{ \alert{$h(t)=f([x(t); h(t-1)])$}}\\
+	\small{ $RNN: \pmb{x}_{t_0} \otimes \pmb{x}_{t_1} \otimes \dots \otimes \pmb{x}_{t_i} \mapsto \pmb{y}_{t_i}$}\\
+	\alert{Finite memory}
 	\end{minipage}
@@
 	\begin{quote}
-	\small \textit{"If training vanilla neural nets is optimization over functions, training recurrent nets is \alert{optimization over programs.}"}
+	\small \textit{"If training vanilla neural nets is optimization over functions, training recurrent nets is \alert{optimization over programs}."}
 	\end{quote}
@@
 \begin{frame}{Approach}
-	Train a RNN to act as a \alert{controller} to interact with a memory matrix M of N (arbitrary many) addresses.
+	Train a RNN to act as the \alert{controller} of a memory matrix M of N 
+	addresses through R \alert{read heads} and one \alert{write head}.
+
 	\pause
@@
 		\begin{itemize} 
-		\item Fill $L \in \{0,1\}^{2N}$ indexing \alert{temporal transitions}
+		\item Fill $L \in [0,1]^{2N}$ indexing \alert{temporal transitions}
 		\item \alert{Shift} operations defined by $LW,\ L^TW$
@@
 
-\begin{frame}{Controller}
+\begin{frame}{Controller: Overview}
 	A deep \alert{long short-term memory network} receiving input:
@@
 
-\begin{frame}{Controller: Signal-Flow}
+\begin{frame}{Controller: Signal-Flow (1/2)}
 	\alert{Single LSTM layer}
@@
 
-\begin{frame}{Controller: Full View}
+\begin{frame}{Controller: Signal-Flow (2/2)}
 	\alert{LSTM Network} (multiple layers)
@@
 		\foreach \name/\x in {h1/3, h2/5, h3/7, hL/10} {\node[inner sep=0] (\name) at (\x, -2) {};}
-		\foreach \name/\x in {s0/3, s1/5, s2/7, sL/10} {\node[split] (\name) at (\x,-3) {$\textcolor{black}{\tiny;}$};}
+		\foreach \name/\x in {s1/5, s2/7, sL/10} {\node[split] (\name) at (\x,-3) {$\textcolor{black}{\tiny;}$};}
 		\foreach \name/\x/\tag in {L1/2/$LSTM_1$, L2/4/$LSTM_2$, L3/6/$LSTM_3$, LL/10/$LSTM_L$} 
@@
 		\draw (dummy_node) -| (LL);
-		\draw (L1) edge[->] (L2);
-		\draw (L2) edge[->] (L3);
-		\draw (L3) edge[->] (Ld);
-		\draw (Ld) edge[->] (LL);
-		\draw[->] (x1) edge (L1.north);
-		\draw[->] (x2) edge (L2.north);
-		\draw[->] (x3) edge (L3.north);
-		\draw[->] (xL) edge (LL.north);
-		\draw[->] (xd) edge (Ld.north);
-		\draw[->] (1,0) |- (s0);
-		\draw[->] (h1) edge (s0);
-		\draw[->] (s0) edge (s1);
-		\draw[->] (h2) edge (s1);
-		\draw[->] (h3) edge (s2);
-		\draw[->] (s1) edge (s2);
-		\draw[->] (s2) edge (sd);
-		\draw[->] (sd) edge (sL);
-		\draw[->] (LL) edge (sL);		
-		\draw[->] (sL) edge (10, -5);
+		\draw (L1) edge[->,thick] (L2);
+		\draw (L2) edge[->,thick] (L3);
+		\draw (L3) edge[->,thick] (Ld);
+		\draw (Ld) edge[->,thick] (LL);
+		\draw[->,thick] (x1) edge (L1.north);
+		\draw[->,thick] (x2) edge (L2.north);
+		\draw[->,thick] (x3) edge (L3.north);
+		\draw[->,thick] (xL) edge (LL.north);
+		\draw[->,thick] (xd) edge (Ld.north);
+		%\draw[->,thick] (1,0) |- (s0);
+		\draw[->,thick] (h1) |- (s1);
+		\draw[->,thick] (h2) edge (s1);
+		\draw[->,thick] (h3) edge (s2);
+		\draw[->,thick] (s1) edge (s2);
+		\draw[->,thick] (s2) edge (sd);
+		\draw[->,thick] (sd) edge (sL);
+		\draw[->,thick] (LL) edge (sL);		
+		\draw[->,thick] (sL) edge (10, -5);
 		% labels
@@
 		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^3}$] (xt) at (7,-2) {};
-		\node[label=below :$\scriptsize\textcolor{white}{[\xx_t;\hh_t^1]}$] (xt) at (4,-3) {};
-		\node[label=below :$\scriptsize\textcolor{white}{[\xx_t;\hh_t^1;\hh_t^2]}$] (xt) at (6,-3) {};
-		\node[label=left :$\scriptsize\textcolor{white}{[\xx_t;\hh_t^1;\dots;\hh_t^L]}$] (xt) at (10,-5) {};
+		\node[label=below :$\scriptsize\textcolor{white}{[\hh_t^1;\hh_t^2]}$] (xt) at (6,-3) {};
+		\node[label=left :$\scriptsize\textcolor{white}{[\hh_t^1;\hh_t^2;\dots;\hh_t^L]}$] (xt) at (10,-5) {};
 	\end{tikzpicture}
@@
 	\pause
-	\alert{Intermediate output} $\pmb{\upsilon}_t$
+	\alert{Intermediate output} $\pmb{\upsilon}_t = W_y[\hh_t^1;\dots;\hh_t^L]$
 	\[
@@
 	\pause
-	\alert{Interface vector} $\pmb\xi_t$
+	\alert{Interface vector} $\pmb{\xi}_t = W_\xi[\hh_t^1;\dots;\hh_t^L]$
 
@@
 
-\begin{frame}{Memory Adressing: RW}
+\begin{frame}{Memory Adressing: Content-Lookup}
+	\alert{R read keys} $\pmb{k}^{r,i} \in \mathbb{R}^W,\ i=1\dots R$\\
+	\alert{R read strengths} $\beta^{r,i} \in [1,\infty),\ i=1\dots R$\\
+	\alert{Write key} $\pmb{k}^{w} \in \mathbb{R}^W$\\
+	\alert{Write strength} $\beta^{w} \in [1,\infty)$
+
+	\pause
+	\alert{Weightings} $w$ given by $\mathcal{C}$
+	\[
+	\mathcal{C}(M,\pmb{k},\beta)[i]= 
+	\frac {exp \{ \mathcal{D} (\pmb{k},M[i,:])\beta \} }
+	{ \sum_{j}{exp \{ \mathcal{D} (\pmb{k},M[j,:])\beta \}}}
+	\]
+
+	\pause
 	\alert{Read operations}
@@
 	\]
-\pause
 	\alert{Write operations}
 	\[
-M_t = M_{t-1} \circ (\pmb{1} - \pmb{w}_t^T\pmb{e}_t^T) + \pmb{w}_t^W\pmb{v}_t^T
+	M_t = M_{t-1} \circ (\pmb{1} - \pmb{w}_t^w\pmb{e}_t^T) + \pmb{w}_t^w\pmb{v}_t^T
 	\]
@@
 	\item \alert{Entity Networks} (Henaff, Weston, Szlam, Bordes, LeCun)
+	\item \alert{End-to-End Memory Networks} (Sukhbaatar, Szlam, Weston, Fergus)	
+	\item \alert{Jointly Learning to Align and Translate} (Bahdanau, Cho, Bengio)
 	\item \alert{Principles of Probabilistic Programming Languages} (Goodman)

### 2018-05-11 Presentation/Presentation.tex
refining equations

@@
 \usepackage{bm}
+\newenvironment{rcases}
+  {\left.\begin{aligned}}
+  {\end{aligned}\right\rbrace}
+
 % Code listing
@@
 	\begin{itemize}
+	\item Inspired by biological memory
+	\item Reimaging of classical concepts of computation
 	\item Extension of NTMs
 	\begin{itemize}
-		\pause
 		\item End-to-end differentiable
-		\pause
 		\item Auto-associative memory
-		\pause
 		\item Turing complete
-		\pause
-		\item[+] Memory attention mechanisms
+		\item[+] Stronger memory management
 	\end{itemize}
-	\pause
-	\item Mimic mammalian biological memory
-	\item Employ classical concepts of computation
 	\end{itemize}
@@
 
-\begin{frame}{Introduction: RNNs}
+\begin{frame}{Introduction: Neural Networks}
 	\begin{minipage}[t]{.44\textwidth}	
@@
 		\begin{itemize}
-		\item \alert{Attention} over memory defined by weightings $W \in \mathbb{R}^N$
+		\item \alert{Attention} over memory defined by weightings $w \in \mathcal{S}^N$
 		\item Compare controller output with memory objects (\alert{auto-associative memory})
@@
 		\begin{itemize} 
-		\item Fill $L \in [0,1]^{2N}$ indexing \alert{temporal transitions}
-		\item \alert{Shift} operations defined by $LW,\ L^TW$
+		\item Fill $L \in [0,1]^{N \times N}$ indexing \alert{temporal transitions}
+		\item \alert{Shift} operations defined by $Lw,\ L^\top w$
 		\end{itemize}
@@
 	\[
-	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots ;\pmb{r}_{t-1}^R]
+	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots ;\pmb{r}_{t-1}^R] \tag{\text{\alert{timestep t}}}
 	\]
@@
 	\[
-	(\pmb{\upsilon}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
+	(\pmb{\upsilon}_T,\pmb{\xi}_T)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta) \tag{\text{\alert{entire sequence}}}
 	\]
@@
 \begin{frame}{Controller: State Equations}
-	A more detailed look into $\mathcal{N}$:\\
+	A more detailed look into $\mathcal{N}$.\\
+
+%	\pause
+%	\begin{equation*}
+%	\begin{rcases}
+%  	\text{\alert{Input}} &: [\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]\\
+%  	\text{\alert{Output}} &: \hh_t^l\\
+%	\end{rcases}
+%	\text{(\alert{Layer \alert{l} at time \alert{t}})}
+%	\end{equation*}
+
+	\pause		
+	\underline{\alert{LSTM layer equations}}
+
+	\alert{Input}: $[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]$ \\
+	\alert{Output}: $\hh_t^l$
+	\pause
 	\begin{align}
-	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
-	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
-	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
-	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
-	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
-	\nonumber \\ 
-	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
-	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
+	\ii_t^l &= \zeta_i([\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]) \tag{\alert{input gate}}\\
+	\ff_t^l &= \zeta_f([\xx_t;\hh_{t-1}^l;\hh_t^{l-1}])	\tag{\alert{forget gate}}\\
+	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^l\zeta_s([\xx_t;\hh_{t_1}^l;\hh_t^{l-1}]) \tag{\alert{state update}}\\
+	\oo_t^l &= \zeta_o([\xx_t;\hh_{t-1}^l;\hh_t^{l-1}])	\tag{\alert{output gate}}\\
+	\hh_t^l &= \oo_t^l\zeta_h(\Ss_t^l)		\tag{\alert{hidden layer}}
 	\end{align}
+%	\nonumber \\ 
+%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
+%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
+%	\end{align}
+%	\begin{align}
+%	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
+%	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
+%	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
+%	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
+%	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
+%	\nonumber \\ 
+%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
+%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
+%	\end{align}
 \end{frame}
@@
 			at (6,6) {\textcolor{black}{$\times$}};
-		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (id) 
-			at (4,8) {\textcolor{black}{$\int$}};
-		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (sd) 
-			at  (4,6) {\small\textcolor{black}{$\int$}};
+		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (id) 
+			at (4,8) {\textcolor{black}{$\zeta_i$}};
+		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (sd) 
+			at  (4,6) {\small\textcolor{black}{$\zeta_s$}};
 		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (o) 
@@
 			at (16,6) {\textcolor{black}{$\times$}};
-		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (od) 
-			at (12,6) {\small\textcolor{black}{$\int$}};
-		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (odd) 
-			at (4,10) {\small\textcolor{black}{$\int$}};
-		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (fd) 
-			at (4,2) {\small\textcolor{black}{$\int$}};
+		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (hd) 
+			at (12,6) {\small\textcolor{black}{$\zeta_h$}};
+		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (odd) 
+			at (4,10) {\small\textcolor{black}{$\zeta_o$}};
+		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (fd) 
+			at (4,2) {\small\textcolor{black}{$\zeta_f$}};
 		% recurrency
@@
 		\draw (ix) edge[->, thick] (s);
-		\draw (s) edge[thick] (od);
-		\draw (od) edge[->, thick] (ox);
+		\draw (s) edge[thick] (hd);
+		\draw (hd) edge[->, thick] (ox);
 		\draw (ox) edge[->, thick] (20,6);
@@
 	\begin{itemize}
-		\item Read keys %$\pmb{k}_t^{r,i} \in \mathbb{R}^W$
-		\item Read strengths %$\beta_t^{r,i} \in [1,\infty)$
-		\item Write key %$\pmb{k}_t^w \in \mathbb{R}^W$	
-		\item Write strength %$\beta_t^{w} \in [1,\infty)$
-		\item Erase vector %$\pmb{e}_t \in [0,1]^W$	
+		\item Read keys: $\pmb{k}_t^{r,i}$ % \in \mathbb{R}^W$
+		\item Read strengths: $\beta_t^{r,i}$ % \in [1,\infty)$
+		\item Write key: $\pmb{k}_t^w$ % \in \mathbb{R}^W$	
+		\item Write strength: $\beta_t^{w}$ % \in [1,\infty)$
+		\item Erase vector: $\pmb{e}_t$ % \in [0,1]^W$	
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Write vector %$\pmb{v}_t \in \mathbb{R}^W$
-		\item Free gates %$\pmb{f}_t^i \in [0,1]$		
-		\item Allocation gate %$g_t^a \in [0,1]$
-		\item Write gate %$g_t^w \in [0,1]$
-		\item Read modes %$\pmb{\pi}_t^i \in \mathcal{S}_3$
+		\item Write vector: $\pmb{v}_t$ % \in \mathbb{R}^W$
+		\item Free gates: $\pmb{\phi}_t^i$ % \in [0,1]$		
+		\item Allocation gate: $g_t^a$ % \in [0,1]$
+		\item Write gate: $g_t^w$ % \in [0,1]$
+		\item Read modes: $\pmb{\pi}_t^i$ % \in \mathcal{S}_3$
 	\end{itemize}
@@
 	\alert{Write key} $\pmb{k}^{w} \in \mathbb{R}^W$\\
-	\alert{Write strength} $\beta^{w} \in [1,\infty)$
+	\alert{Write strength} $\beta^{w} \in [1,\infty)$\\
 
 	\pause
-	\alert{Weightings} $w$ given by $\mathcal{C}$
+	\alert{Matching function} $\mathcal{D}$ comparing memory contents
+
+	\pause
+	\alert{Weighting function} $\mathcal{C}$ normalizing and sharpening matches
 	\[
 	\mathcal{C}(M,\pmb{k},\beta)[i]= 
-	\frac {exp \{ \mathcal{D} (\pmb{k},M[i,:])\beta \} }
-	{ \sum_{j}{exp \{ \mathcal{D} (\pmb{k},M[j,:])\beta \}}}
+	\frac {exp \{\beta\mathcal{D} (\pmb{k},M[i,:])\} }
+	{ \sum_{j}{exp \{\beta\mathcal{D} (\pmb{k},M[j,:]) \}}}
 	\]
+\end{frame}
+
+\begin{frame}{Memory Adressing: R/W}
+	\alert{Attention} dictated by weightings $\pmb{w} \in \mathcal{S}^N$\\
+	\alert{Erase vector} $\pmb{e}_t \in [0,1]^W$\\
+	\alert{Write vector} $\pmb{v}_t \in \mathbb{R}^W$\\
+
+	\alert{Read operations}
+	\begin{align*}
+	 \pmb{r}_t^i = M_t^\top\pmb{w}_t^{r,i}\\
+	\end{align*}
 
 	\pause
-	\alert{Read operations}
-	\[
-	\pmb{r}_t^i = M_t^T\pmb{w}_t^{r,i}
-	\]
 	\alert{Write operations}
-	\[
-	M_t = M_{t-1} \circ (\pmb{1} - \pmb{w}_t^w\pmb{e}_t^T) + \pmb{w}_t^w\pmb{v}_t^T
-	\]
+	\begin{align*}
+	M_t = \underbrace{M_{t-1} \circ (\pmb{1} - \pmb{w}_t^w\pmb{e}_t^\top)}_{\text{erased memory}} + 
+	\underbrace{\pmb{w}_t^w\pmb{v}_t^\top}_{\text{new write}}
+	\end{align*}
+\end{frame}
+
+\begin{frame}{Memory Adressing: Dynamic Allocation}
+	\alert{Free gates} $\pmb{\phi}_t^i \in [0,1]^W$\\
+	\alert{Allocation gate} $g_t^a \in [0,1]$\\
+	\alert{Write gate} $g_t^w \in [0,1]$\\
+
+	\alert{"Free list" scheme}
+	\begin{align*}
+	\pmb{\psi}_t &= \prod\limits_{i=1}^R (\pmb{1} - \pmb{\phi}_t^iw_{t-1}^{r,i}) \tag{\alert{memory retention}}\\
+	u_t &= (\pmb{u}_{t-1} + \pmb{w}_{t-1}^w + \pmb{u}_{t-1} \circ \pmb{w}_{t-1}^w) \circ \pmb{\psi}_t \tag{\alert{usage tracking}}\\
+	\end{align*}
+
+	\pause
+	\alert{Attention shift} 
+	\begin{itemize}
+	\item Obtain the \alert{allocation vector} $\pmb{a}_t$ by normalizing $\pmb{u}_t$\\
+	\item \alert{Shift} $\pmb{w}_t$ by $g_t^a\pmb{a}_t$ and \alert{scale} by $g_t^w$
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Memory Adressing: Temporal Linking}
+	\alert{Free gates} $\pmb{\phi}_t^i \in [0,1]^W$\\
+
+	\alert{Memory retention}
+	\begin{align*}
+	\pmb{\psi}_t = \prod\limits_{i=1}^R (\pmb{1} - \pmb{\phi}_t^iw_{t-1}^{r,i}) \\
+	\end{align*}
+
+	\pause
+	\alert{Usage tracking}
+	\begin{align*}
+	u_t = (\pmb{u}_{t-1} + \pmb{w}_{t-1}^w + \pmb{u}_{t-1} \circ \pmb{w}_{t-1}^w) \circ \pmb{\psi}_t\\
+	\end{align*}
+
+	\pause
+	\alert{Allocation vector} $\pmb{a}_t$ given by normalizing and sorting $\pmb{u}_t$
 \end{frame}
@@
 
+\begin{frame}{Conclusion}
+	\alert{Takeaway}\\
+	We can automatically infer simple functions over complex data structures, in the form of \alert{probability distributions} just by using examples.\\
+
+	\pause
+	\center	\alert{Thank you!}
+\end{frame}
+
 \end{document}

### 2018-05-14 Presentation/Presentation.tex
less math

@@
 \newcommand{\Ss}{\pmb{s}}
+\newcommand{\Cc}{\pmb{c}}
 \newcommand{\bb}{\pmb{b}}
@@
 	\begin{itemize}
-	\item Inspired by biological memory
+	\item Functional replication of biological memory
 	\item Reimaging of classical concepts of computation
@@
 		\item Turing complete
-		\item[+] Stronger memory management
+		\item[+] Computationally efficient memory management
 	\end{itemize}
@@
 	\[
-	(\pmb{\upsilon}_T,\pmb{\xi}_T)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta) \tag{\text{\alert{entire sequence}}}
+	(\pmb{\upsilon}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_t];\vartheta) \tag{\text{\alert{entire sequence}}}
 	\]
-	where $\mathcal{N}$ a set of state equations and $\vartheta$ their trainable parameters.
+	where \alert{$\mathcal{N}$} a set of state equations and \alert{$\vartheta$} their trainable parameters.
 \end{frame}
 
-\begin{frame}{Controller: State Equations}
-	A more detailed look into $\mathcal{N}$.\\
+\begin{frame}{LSTM: Overview}
+	\alert{LSTM Network}\\
+	Multiple stacked LSTM units.
 
-%	\pause
-%	\begin{equation*}
-%	\begin{rcases}
-%  	\text{\alert{Input}} &: [\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]\\
-%  	\text{\alert{Output}} &: \hh_t^l\\
-%	\end{rcases}
-%	\text{(\alert{Layer \alert{l} at time \alert{t}})}
-%	\end{equation*}
+	\alert{LSTM Unit}\\
+	A RNN that has an intrinsic memory \alert{cell} $\Cc_t^l$ and three \alert{gates}.
 
 	\pause
-	\underline{\alert{LSTM layer equations}}
+	\begin{enumerate}
+	\item \alert{Input gate} $\ii_t^l$ %regulating flow to the memory cell
+	\item \alert{Forget gate} $\ff_t^l$ %selectively erasing memory cell contents
+	\item \alert{Output gate} $\oo_t^l$ %regulating flow from the memory cell to the output
+	\end{enumerate}
 
-	\alert{Input}: $[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]$ \\
-	\alert{Output}: $\hh_t^l$
-	\pause
-	\begin{align}
-	\ii_t^l &= \zeta_i([\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]) \tag{\alert{input gate}}\\
-	\ff_t^l &= \zeta_f([\xx_t;\hh_{t-1}^l;\hh_t^{l-1}])	\tag{\alert{forget gate}}\\
-	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^l\zeta_s([\xx_t;\hh_{t_1}^l;\hh_t^{l-1}]) \tag{\alert{state update}}\\
-	\oo_t^l &= \zeta_o([\xx_t;\hh_{t-1}^l;\hh_t^{l-1}])	\tag{\alert{output gate}}\\
-	\hh_t^l &= \oo_t^l\zeta_h(\Ss_t^l)		\tag{\alert{hidden layer}}
-	\end{align}
-%	\nonumber \\ 
-%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
-%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
-%	\end{align}
-%	\begin{align}
-%	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
-%	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
-%	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
-%	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
-%	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
-%	\nonumber \\ 
-%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
-%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
-%	\end{align}
 \end{frame}
 
-\begin{frame}{Controller: Signal-Flow (1/2)}
-	\alert{Single LSTM layer}
+\begin{frame}{LSTM: Signal-Flow (1/2)}
+	\alert{LSTM Unit} (single layer)
+	\begin{itemize}
+	\item	\alert{Input}: $[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]$\\
+	\item	\alert{Output}: $\hh_t^l$\\	
+	\end{itemize}
+
+	\pause
+	\vspace{-10pt}
 	\begin{figure}
-	\begin{tikzpicture}[scale=0.5]
+	\begin{tikzpicture}[scale=0.45]
 		%-------------------------------------------------------------------------------
@@
 		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (s) 
-			at (9,6) {\large\textcolor{black}{$\Ss_t^l$}};
+			at (9,6) {\large\textcolor{black}{$\Cc_t^l$}};
 		\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=white] (fx) 
@@
 		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (sd) 
-			at  (4,6) {\small\textcolor{black}{$\zeta_s$}};
+			at  (4,6) {\small\textcolor{black}{$\zeta_c$}};
 		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (o) 
@@
 		% labels
+%		\node[label=above:$\textcolor{white}{\mathcal{I}}$] (we) at (1,6) {};		
 		\node[label=below:$\textcolor{white}{\hh_t^{l-1}}$] (ht1) at (-1,4) {};
@@
 	\alert{LSTM Network} (multiple layers)
+	\begin{itemize}
+	\item	\alert{Input}: $\xx_t$\\
+	\item	\alert{Output}: $[\hh_t^1;\hh_t^2;\dots\hh_t^L]$\\	
+	\end{itemize}
+	\pause
 	\begin{figure}
@@
 	\tikzset{split/.style={circle, draw=black,inner sep=0pt, minimum size = 3mm, fill=white}}
-		\node (dummy_node) at (0,0) {};
+		\node (dummy_node) at (1,0) {};
 		\foreach \name/\x in {x1/2, x2/4, x3/6, xd/8, xL/10} {\node[inner sep=0] (\name) at (\x,0) {};}
 		\foreach \name/\x in {h1/3, h2/5, h3/7, hL/10} {\node[inner sep=0] (\name) at (\x, -2) {};}
-		\foreach \name/\x in {s1/5, s2/7, sL/10} {\node[split] (\name) at (\x,-3) {$\textcolor{black}{\tiny;}$};}
+		\foreach \name/\x in {s1/5, s2/7, sL/11} {\node[split] (\name) at (\x,-3) {$\textcolor{black}{\tiny;}$};}
 		\foreach \name/\x/\tag in {L1/2/$LSTM_1$, L2/4/$LSTM_2$, L3/6/$LSTM_3$, LL/10/$LSTM_L$} 
@@
 		\node (Ld) at (8,-2) {$\dots$};
-		\node (sd) at (8,-3) {$\dots$};
+		\node (sd) at (9,-3) {$\dots$};
 		\draw (dummy_node) -| (LL);
@@
 		\draw[->,thick] (sd) edge (sL);
-		\draw[->,thick] (LL) edge (sL);		
-		\draw[->,thick] (sL) edge (10, -5);
+		\draw[->,thick] (LL) -| (sL);		
+		\draw[->,thick] (sL) edge (11, -4);
+		\draw (L1.east) [->, densely dotted, thick, gray!90] .. controls +(0.6,-0.8) and +(-0.6,-0.8) .. (L1.south);
+		\draw (L2.east) [->, densely dotted, thick, gray!90] .. controls +(0.6,-0.8) and +(-0.6,-0.8) .. (L2.south);
+		\draw (LL.east) [->, densely dotted, thick, gray!90] .. controls +(0.6,-0.8) and +(-0.6,-0.8) .. (LL.south);
 		% labels
-		\node[label=above right :$\scriptsize\textcolor{white}{\xx_t}$] (xt) at (0,0) {};
+		\node[label=above right :$\scriptsize\textcolor{white}{\xx_t}$] (xt) at (1,0) {};
 		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^1}$] (xt) at (3,-2) {};
@@
 		\node[label=below :$\scriptsize\textcolor{white}{[\hh_t^1;\hh_t^2]}$] (xt) at (6,-3) {};
-		\node[label=left :$\scriptsize\textcolor{white}{[\hh_t^1;\hh_t^2;\dots;\hh_t^L]}$] (xt) at (10,-5) {};
+		\node[label=left :$\scriptsize\textcolor{white}{[\hh_t^1;\hh_t^2;\dots;\hh_t^L]}$] (xt) at (11,-4) {};
 	\end{tikzpicture}
@@
 \begin{frame}{Memory Adressing: Temporal Linking}
-	\alert{Free gates} $\pmb{\phi}_t^i \in [0,1]^W$\\
 
-	\alert{Memory retention}
-	\begin{align*}
-	\pmb{\psi}_t = \prod\limits_{i=1}^R (\pmb{1} - \pmb{\phi}_t^iw_{t-1}^{r,i}) \\
-	\end{align*}
-
-	\pause
-	\alert{Usage tracking}
-	\begin{align*}
-	u_t = (\pmb{u}_{t-1} + \pmb{w}_{t-1}^w + \pmb{u}_{t-1} \circ \pmb{w}_{t-1}^w) \circ \pmb{\psi}_t\\
-	\end{align*}
-
-	\pause
-	\alert{Allocation vector} $\pmb{a}_t$ given by normalizing and sorting $\pmb{u}_t$
 \end{frame}
@@
 	\alert{Takeaway}\\
-	We can automatically infer simple functions over complex data structures, in the form of \alert{probability distributions} just by using examples.\\
+	We can automatically infer simple functions over complex data structures in the form of \alert{probability distributions}, just by using examples!\\
 
@@
 
+\begin{frame}{LSTM: State Equations}
+
+	\begin{align}
+	\ii_t^l &= \zeta_i(\mathcal{I}) \tag{\alert{input gate}}\\
+	\ff_t^l &= \zeta_f(\mathcal{I})	\tag{\alert{forget gate}}\\
+	\Cc_t^l &= \ff_t^l\Cc_{t-1}^l + \ii_t^l\zeta_c(\mathcal{I}) \tag{\alert{memory cell}}\\
+	\oo_t^l &= \zeta_o(\mathcal{I})	\tag{\alert{output gate}}\\
+	\hh_t^l &= \oo_t^l\zeta_h(\Cc_t^l)		\tag{\alert{hidden layer}}
+	\end{align}
+%	\nonumber \\ 
+%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
+%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
+%	\end{align}
+%	\begin{align}
+%	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
+%	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
+%	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
+%	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
+%	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
+%	\nonumber \\ 
+%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
+%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
+%	\end{align}
+\end{frame}
+
 \end{document}

### 2018-05-16 Presentation/Presentation.tex
?

@@
 \begin{frame}{Approach}
-	Train a RNN to act as the \alert{controller} of a memory matrix M of N 
-	addresses through R \alert{read heads} and one \alert{write head}.
+	Train a RNN to act as the \alert{controller} of a memory matrix $M \in \mathbb{R}^{N\times W}$ through R \alert{read heads} and one \alert{write head}.
 
@@
 		\begin{itemize}
-		\item Mark memory locations with $\{0,1\}$ to \alert{signal usage}
+		\item Mark memory locations with $\pmb{u} \in [0,1]^N$ to \alert{signal usage}
 		\item Manipulate signals during R/W operations to enable \alert{reallocation}
@@
 	\pmb{\psi}_t &= \prod\limits_{i=1}^R (\pmb{1} - \pmb{\phi}_t^iw_{t-1}^{r,i}) \tag{\alert{memory retention}}\\
-	u_t &= (\pmb{u}_{t-1} + \pmb{w}_{t-1}^w + \pmb{u}_{t-1} \circ \pmb{w}_{t-1}^w) \circ \pmb{\psi}_t \tag{\alert{usage tracking}}\\
+	u_t &= (\pmb{u}_{t-1} + \pmb{w}_{t-1}^w - \pmb{u}_{t-1} \circ \pmb{w}_{t-1}^w) \circ \pmb{\psi}_t \tag{\alert{usage tracking}}\\
 	\end{align*}
@@
 \begin{frame}{Memory Adressing: Temporal Linking}
+	\alert{Read modes}: $\pmb{\pi}_t^i \in \mathcal{S}_3$\\
 
+	\pause
+	\alert{Temporal Transition} $\pmb{L}_t \in [0,1]^{N\times N}$
+	\[
+	\pmb{L}[i,j] = \underbrace{(1 - w_t^W[i] - w_t^W[j])\pmb{L}_{t-1}[i,j]}_{\text{\tiny{{Part of last transition}}}} + \underbrace{w_t^w[i]w_{t-1}^w[j]}_{\text{\tiny{Current transition}}}
+%	\pmb{p}_t = (1 - \sum\limits_{i}\pmb{w}_t^W[i])\pmb{p}_{t-1} + \pmb{w}_t^W
+	\]
+
+	\pause
+	\alert{Mode Interpolation}
+	\[
+	\pmb{w}_t^{r,i} = 
+					\underbrace{\pmb{\pi}_t^i[1]L\pmb{w}_t^{r,i}}_{\text{\tiny{Forward shift}}} + 
+					\underbrace{\pmb{\pi}_t^i[2]\pmb{w}_t^{r,i}}_{\text{\tiny{No shift}}} + 
+					\underbrace{\pmb{\pi}_t^i[3]L^\top\pmb{w}_t^{r,i}}_{\text{\tiny{Backward shift}}} 
+	\]
 \end{frame}
 
-\begin{frame}{Further Reading}
+\begin{frame}{Conclusion}
+	\alert{Recap}\\
+	We can simulate computation and expand upon it by using differentiable, continuous operations.
+
+	\pause
+	\alert{Takeaway}\\
+	We can automatically infer simple functions over complex data structures in the form of \alert{probability distributions}, just by using examples!\\
+\end{frame}
+
+\begin{frame}{Appendix: LSTM Equations}
+
+%	\begin{align}
+%	\ii_t^l &= \zeta_i(\mathcal{I}) \tag{\alert{input gate}}\\
+%	\ff_t^l &= \zeta_f(\mathcal{I})	\tag{\alert{forget gate}}\\
+%	\Cc_t^l &= \ff_t^l\Cc_{t-1}^l + \ii_t^l\zeta_c(\mathcal{I}) \tag{\alert{memory cell}}\\
+%	\oo_t^l &= \zeta_o(\mathcal{I})	\tag{\alert{output gate}}\\
+%	\hh_t^l &= \oo_t^l\zeta_h(\Cc_t^l)		\tag{\alert{hidden layer}}
+%	\end{align}
+%	\nonumber \\ 
+%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
+%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
+%	\end{align}
+	\begin{align}
+	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
+	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
+	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
+	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
+	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
+	\nonumber \\ 
+	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
+	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
+	\end{align}
+\end{frame}
+
+\begin{frame}{Appendix: Further Reading}
+	\begin{minipage}{0.49\textwidth}
+	\underline{\alert{Neural Architectures}}
 	\begin{itemize}
-	\item \alert{Neural Turing Machines} (Graves, Wayne, Danihelka)
-	\item \alert{Entity Networks} (Henaff, Weston, Szlam, Bordes, LeCun)
-	\item \alert{End-to-End Memory Networks} (Sukhbaatar, Szlam, Weston, Fergus)	
-	\item \alert{Jointly Learning to Align and Translate} (Bahdanau, Cho, Bengio)
+	\item \alert{Learning to Forget}\\ (Gers, Schmidhuber, Cummins)
+	\item \alert{Neural Turing Machines}\\ (Graves, Wayne, Danihelka)
+	\item \alert{Entity Networks}\\ (Henaff, Weston, Szlam, Bordes, LeCun)
+	\item \alert{End-to-End Memory Networks}\\ (Sukhbaatar, Szlam, Weston, Fergus)	
+	%\item \alert{Jointly Learning to Align and Translate}\\ (Bahdanau, Cho, Bengio)
+	%\item \alert{Principles of Probabilistic Programming Languages} (Goodman)
+	%\item \alert{Backprop as a Functor} (Fong, Spivak, Tuyéras)
+	%\item \alert{Formal Methods for Probabilistic Programming} (Selsam, Liang, Dill)
+	\end{itemize}
+	\end{minipage}
+	\begin{minipage}{0.49\textwidth}
+	\begin{itemize}	
+	\item \alert{Jointly Learning to Align and Translate}\\ (Bahdanau, Cho, Bengio)
+	\end{itemize}
+	\underline{\alert{Probabilistic Programming}}
+	\begin{itemize}
 	\item \alert{Principles of Probabilistic Programming Languages} (Goodman)
@@
 	\end{itemize}
-\end{frame}
-
-\begin{frame}{Conclusion}
-	\alert{Takeaway}\\
-	We can automatically infer simple functions over complex data structures in the form of \alert{probability distributions}, just by using examples!\\
-
-	\pause
-	\center	\alert{Thank you!}
-\end{frame}
-
-\begin{frame}{LSTM: State Equations}
-
-	\begin{align}
-	\ii_t^l &= \zeta_i(\mathcal{I}) \tag{\alert{input gate}}\\
-	\ff_t^l &= \zeta_f(\mathcal{I})	\tag{\alert{forget gate}}\\
-	\Cc_t^l &= \ff_t^l\Cc_{t-1}^l + \ii_t^l\zeta_c(\mathcal{I}) \tag{\alert{memory cell}}\\
-	\oo_t^l &= \zeta_o(\mathcal{I})	\tag{\alert{output gate}}\\
-	\hh_t^l &= \oo_t^l\zeta_h(\Cc_t^l)		\tag{\alert{hidden layer}}
-	\end{align}
-%	\nonumber \\ 
-%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
-%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
-%	\end{align}
-%	\begin{align}
-%	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
-%	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
-%	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
-%	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
-%	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
-%	\nonumber \\ 
-%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
-%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
-%	\end{align}
+	\end{minipage}
 \end{frame}

### 2018-05-23 Presentation/Presentation.tex
meh
(almost) final

@@
 	\item Data Flow Programming
-	\item Bayesian Reasoning
-	\item Machine Learning
+	\item Bayesian Reasoning / Machine Learning
+	\item Fuzzy Logic
 	\item Functional Programming
@@
 	%\small \alert{$y=g(h),\ h=f(x)$}\\
-	\small $NN: \pmb{x}_{t_i} \mapsto \pmb{y}_{t_i}$\\
+	\small $NN: \pmb{x}_{t} \mapsto \pmb{y}_{t}$\\
 	\alert{No memory}
@@
 	%\small{ \alert{$h(t)=f([x(t); h(t-1)])$}}\\
-	\small{ $RNN: \pmb{x}_{t_0} \otimes \pmb{x}_{t_1} \otimes \dots \otimes \pmb{x}_{t_i} \mapsto \pmb{y}_{t_i}$}\\
+	\small{ $RNN: \pmb{x}_{0} \otimes \pmb{x}_{1} \otimes \dots \otimes \pmb{x}_{t} \mapsto \pmb{y}_{t}$}\\
 	\alert{Finite memory}
@@
 	\[
-	(\pmb{\upsilon}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_t];\vartheta) \tag{\text{\alert{entire sequence}}}
+	(\pmb{y}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_t];\vartheta) \tag{\text{\alert{entire sequence}}}
 	\]
@@
 	\[
-	(\pmb{\upsilon}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
+	(\pmb{y}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
 	\]
@@
 	\pause
-	\alert{Intermediate output} $\pmb{\upsilon}_t = W_y[\hh_t^1;\dots;\hh_t^L]$
-	\[
-	\pmb{y}_t = \pmb{\upsilon}_t + W_R[\pmb{r}_t^1;\dots;\pmb{r}_t^R] \tag{\alert{Memory-conditioning}}
-	\]
+	\alert{User output} $\pmb{y}_t = W_y[\hh_t^1;\dots;\hh_t^L]$
+%	\[
+%	\pmb{y}_t = \pmb{\upsilon}_t + W_R[\pmb{r}_t^1;\dots;\pmb{r}_t^R] \tag{\alert{Memory-conditioning}}
+%	\]
 
@@
 	\begin{align*}
-	 \pmb{r}_t^i = M_t^\top\pmb{w}_t^{r,i}\\
+	 \pmb{r}_t^i = M_t^\top\pmb{w}_t^{r,i} \\ 
 	\end{align*}
@@
 
+\begin{frame}{Experiments}
+	\begin{itemize}
+	\item \alert{Language Tasks}
+	\begin{itemize}
+	\item Inference
+	\item Logical Reasoning
+	\end{itemize}
+	\pause
+	\item \alert{Graph Tasks}
+	\begin{itemize}
+	\item Network Traversal
+	\item Policy Learning
+	\end{itemize}
+	\end{itemize}
+\end{frame}
+
 \begin{frame}{Conclusion}
 	\alert{Recap}\\
-	We can simulate computation and expand upon it by using differentiable, continuous operations.
+	\begin{itemize}
+	\item We can simulate computation and expand upon it by using differentiable, continuous operations.\\
+	\item[] We can automatically infer simple functions over complex data structures in the form of \alert{probability distributions}, just by using examples!\\
+	\end{itemize}
+\end{frame}
 
-	\pause
-	\alert{Takeaway}\\
-	We can automatically infer simple functions over complex data structures in the form of \alert{probability distributions}, just by using examples!\\
+\begin{frame}{Thank you!}
+	\centering
+	\alert{Questions?}
 \end{frame}

### 2018-05-25 Presentation/Presentation.tex
changes according to feedback

@@
 			at (6,6) {\textcolor{black}{$\times$}};
-		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (id) 
+		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=gray!70] (id) 
 			at (4,8) {\textcolor{black}{$\zeta_i$}};
-		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (sd) 
+		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=gray!70] (sd) 
 			at  (4,6) {\small\textcolor{black}{$\zeta_c$}};
@@
 			at (16,6) {\textcolor{black}{$\times$}};
-		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (hd) 
+		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=gray!70] (hd) 
 			at (12,6) {\small\textcolor{black}{$\zeta_h$}};
-		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (odd) 
+		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=gray!70] (odd) 
 			at (4,10) {\small\textcolor{black}{$\zeta_o$}};
-		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=white] (fd) 
+		\node[rectangle, draw=black, inner sep=0pt,minimum size=4mm,fill=gray!70] (fd) 
 			at (4,2) {\small\textcolor{black}{$\zeta_f$}};
@@
 	\item We can simulate computation and expand upon it by using differentiable, continuous operations.\\
-	\item[] We can automatically infer simple functions over complex data structures in the form of \alert{probability distributions}, just by using examples!\\
+	\item Simple programs (over complex data structures) can now be automagically inferred.\\
 	\end{itemize}

### 2018-06-03 Paper/Paper.tex
up to DNC

\documentclass[]{article}
\usepackage[a4paper]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathabx}
\usepackage{graphics}
%\usepackage{mathtools}
\usepackage{tikz}
\usepackage{array}
\usepackage{proof}
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\usepackage{subcaption}

\begin{document}
\author{Konstantinos Kogkalidis [6230067]}
\title{Recent Advancements in Neural Computation: \\
\large Differentiable Neural Computers and End-To-End Memory Networks}
\maketitle

\section{Introduction}
In the last decade, neural networks have considerably revolutionized computation and artificial intelligence. Neural networks have been setting new benchmarks in tasks from a broad range of fields, including computer vision, natural language processing and pattern recognition; many of these tasks previously unsolved, and some of these benchmarks surpassing human-level performance. Until recently, this astounding potential has for the most part been limited to tasks involving sensory processing and representation learning. Memory-centric tasks, i.e. tasks requiring data storage and retrieval, have however proven difficult for neural networks to model. This paper serves as a literature review of two recent approaches towards bypassing this limitation, namely Differentiable Neural Computers (DNCs) and End-to-End Memory Networks. The rest of this section will briefly introduce some important background concepts, before the models' details are examined in sections 2 and 3, respectively. Section 4 provides a short discussion and a comparative analysis on the two approaches, and section 5 presents some concluding remarks.

A particularly interesting subclass of neural networks are \textit{Recurrent Neural Networks} (RNNs). Unlike traditional networks, which accept a fixed-size input vector and produce a fixed-size output vector over a finite number of computational steps, RNNs instead operate on sequences of vectors. This additional axis is captured by allowing the RNN to accept one vector at a time and construct an intermediate representation of it, which then combines with the next input vector to affect the computation of the next such representation (Fig.\ref{fig:1}). This elegant addition accounts for a drastic improvement in the representational capacity of the network. Whereas a simple net acts as a fixed function, a RNN acts as a program operating on sequences of inputs. Under this viewpoint, the RNN's hidden representation can be perceived as the program's internal variables, updating as new inputs are received and affecting the computation as it progresses.

\begin{figure}[h!]
\begin{minipage}{0.5\textwidth}
	\centering
	\begin{tikzpicture}[scale=0.5]
		\foreach \y /\alph/\name in {
			0/x1/$x_1$,
		  	-1/x2/$x_2$,
		  	-2/x3/$x_3$,
		  	-4/xM/$x_M$
		 }{
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{black}{\name}};
		 }
		 \node (x..) at (0,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			1/h1/$h_1$,
		  	0/h2/$h_2$,
		  	-1/h3/$h_3$,
		  	-5/hN/$h_N$
		 }{
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (4,\y) {\tiny \textcolor{black}{\name}};
		 }
		 \node (h..) at (4,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			0/y1/$y_1$,
		  	-1/y2/$y_2$,
		  	-2/y3/$y_3$,
		  	-4/yP/$y_P$
		 }{
		 	\node[circle, draw=gray!90,inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (8,\y) {\tiny \textcolor{black}{\name}};
		 }
		 \node (y..) at (8,-3) {\tiny {\vdots}};
		 \foreach \x in {x1, x2, x3, xM}
		 {\foreach \h in {h1, h2, h3, hN}
		 {\draw (\x) edge[gray!90] (\h);}}
		 \foreach \x in {h1, h2, h3, hN}
		 {\foreach \y in {y1, y2, y3, yP}
		 {\draw (\x) edge[gray!90] (\y);}}
	\end{tikzpicture}
	\subcaption{Simple Neural Net}
	\end{minipage}
	\begin{minipage}{0.5\textwidth}
	\centering
	\begin{tikzpicture}[scale=.5]
		\foreach \y /\alph/\name in {
			0/x1/$x_1$,
		  	-1/x2/$x_2$,
		  	-2/x3/$x_3$,
		  	-4/xM/$x_M$
		 }{
		% 	\node[] (\alph) at (0,\y) {\name};
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{black}{\name}};
		 }
		 \node (x..) at (0,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			1/h1/$h_1$,
		  	0/h2/$h_2$,
		  	-1/h3/$h_3$,
		  	-5/hN/$h_N$
		 }{
		 	\node[circle, draw=black, inner sep=0pt,minimum size=3mm,fill=gray!20] (\alph) at (4,\y) {\tiny \textcolor{black}{\name}};
		 }
		 \node (h..) at (4,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			0/y1/$y_1$,
		  	-1/y2/$y_2$,
		  	-2/y3/$y_3$,
		  	-4/yP/$y_P$
		 }{
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (8,\y) {\tiny \textcolor{black}{\name}};
		 }
		 \node (y..) at (8,-3) {\tiny {\vdots}};
		 \foreach \x in {x1, x2, x3, xM}
		 {\foreach \h in {h1, h2, h3, hN}
		 {\draw (\x) edge[gray!90] (\h);}}
		 \foreach \x in {h1, h2, h3, hN}
		 {\foreach \y in {y1, y2, y3, yP}
		 {\draw (\x) edge[gray!90] (\y);}}
		 \draw (h1.east) [->, densely dotted, thick, black] .. controls +(0.8,0.8) and +(-0.8,0.8) .. (h1.west);
		 \draw (h1.east) [->, densely dotted, thick, black] .. controls +(0.4,-0.8) and +(-0.4,0.8) .. (h2.west);
		 \draw (h1.east) [->, densely dotted, thick, black] .. controls +(1,-1.6) and +(-0.6,0.4) .. (h3.west);
		 \draw (h1.east) [->, densely dotted, thick, black] .. controls +(2,-2) and +(-2,2) .. (hN.west);
\end{tikzpicture}
	\subcaption{Recurrent Neural Network}
	\end{minipage}
	\caption[Hello world]
	{\small \textit{Comparison between a simple neural network and a RNN. (a) The simple network applies two transformations $\pmb{x} \mapsto \pmb{h}$ and $\pmb{h} \mapsto \pmb{y}$, the composition of which can be seen as a function $\pmb{x} \mapsto \pmb{y}$. (b) The recurrent network allows through-time connections, depicted with the dotted lines, such that $\pmb{x}_t \times \pmb{h}_{t-1} \mapsto \pmb{h}_t$. The output then becomes a function of the full sequence of inputs received: $\underbrace{\pmb{x}_0 \times \pmb{x}_1 \times \dots \times \pmb{x}_t}_{\text{Sequence Length}} \mapsto \pmb{y}_t$.}\label{fig:1}}
\end{figure}

Although RNNs have been introduced more than three decades ago, their potential was only recognized recently, as the availability of computational power surged. Their ability to model sequential patterns and their interesting properties have garnered a lot of attention, yet they still suffer from two major drawbacks. The first relates to the statefulness achieved by their intermediate representation; even though it is distributed, the hidden vector's size is finite and fixed, therefore capable of only limited, lossy storage. The second is a more intrinsic one and is not only tied to RNNs but neural networks in general; there is no separation between memory and processing, as each neuron is simultaneously a minimal storage unit and a computational one. Although appealing from a biological perspective, this goes against the von Neumann model and our programming paradigm.

A series of advancements has seeked to enhance RNNs with stronger memory management. Starting with the introduction of the \textit{Long Short-Term Memory}, which permits finite storage over arbitrary long computations, research in RNNs has bloomed towards many different directions. One particularly exciting recent advancement is the so-called \textit{attentional interface}, which allows a network to selectively shift its focus on particular indices over a set of dimensions of an arbitrary tensor, thus enabling content-based adressing. The implications of this seemingly simple trick are tremendous; when employing fully differentiable attention (soft-attention), a network can learn how to pick out and combine relevant elements out of a (potentially very large) tensor, instead of lossily encoding it. This translates to arbitrary information retrieval; in other words, the same representations can now have different effects on the computation depending on the present context, similar to how a computer program would refer only to the variables dictated by its currently run instruction. Since its inception, attention has been a key-concept in many influential publication; the creative liberty it is offering, in terms of new potential operations, has also paved the way for architectures which decouple storage from computation. Such architectures, including but not limited to the two presented in this paper, utilize large external matrices and employ attention to perform read and write operations on them.

\section{Notation and Preliminaries}
Given the technical nature of the works presented, it is important to establish a notational common ground. The $(N-1)$-simplex, i.e. the set of all variations of $N$ non-negative scalars that sum up to 1, will be indicated by $\mathcal{S}^N$. A vector will be denoted by a boldface lower letter, e.g. $\pmb{v}$, whereas a matrix will be indicated by a boldface capital letter, e.g. $\pmb M$. Vector concatenation, i.e. merging together N vectors in the order they are given to a create a new, long vector is denoted by a bracketing of vectors separated by the semicolon, e.g. $[\pmb{x}; \pmb{y}; \pmb{z}]$ reads as the concatenation of $\pmb x$, $\pmb y$ and $\pmb z$. When using the comma rather than the semicolon, the notation instead presents a sequence of vectors, e.g. $[\pmb a _1, \dots ,\pmb a _N]$ denotes a sequence of vectors $\pmb a _1$ to $\pmb a _N$. A subscript on a vector or matrix is used to index a single temporal instance from a sequence of such vectors or matrices, e.g. $\pmb{a}_i$ refers to the instance at timestep $i$ of the time-varying vector sequence $[\pmb a _1 , \dots ]$. It should not be confused with intra-vector or matrix indexing, i.e. singling out particular elements out of a vector or matrix, which is denoted by $\pmb a [i]$ and reads as the i-th element of a vector $\pmb a$. Finally, a reminder that a matrix $\pmb M \in \mathbb{R}^{K\times L}$ can be seen as a linear map $M: \mathbb{R}^L \to \mathbb{R}^K$; linear application of $\pmb v \in \mathbb{R}^V $ on $\pmb M \in \mathbb{R}^{M \times V}$ (or matrix-vector multiplication) is thus simply denoted $\pmb {Mv}$.

\section{Differentiable Neural Computers}
\subsection{Description}
Inspired by the von Neumann architecture, DNCs model computation as the interfacing between two units; a RNN controller and an external memory matrix, functioning analogously to the CPU and the RAM, respectively. The memory matrix can be adressed using soft attention mechanisms, allowing selective reading and writing. As both the controller and the interfacing are differentiable, the full architecture is end-to-end differentiable, essentially allowing it to be trained purely with data and minimal human supervision. As the system is already equiped with the necessary tools to simulate traditional computation, i.e. adressing mechanisms, information storage and retrieval, logical flows and arithmetic processing, a DNC in training is  learning the instructions of a program rather than the parameters of a function, and a trained DNC should be able to mimic the behavior of a traditionally hand-written program.

\subsection{Architecture}
\paragraph{Overview} 
A differentiable neural computer consists of two main components; a recurrent neural network \textbf{controller network} and an external \textbf{memory matrix} $M \in \mathbb{R}^{N\times W}$. The matrix contains $N$ memory adresses, each of size $W$, which can be read by the controller through $R$ \textit{read heads}, or written to by one \textit{write head}. At timestep t, the system as a whole receives input in the form of a vector, $\pmb{x}_t \in \mathbb{R}^X$, and produces output in the form of a vector, $\pmb{y}_t \in \mathbb{R}^Y$. The input may be samples from any dataset environment, e.g. some encoding of sensory signals. The output can either represent an approximation for a target vector $\pmb{z}_t \in \mathbb{R}^Y$ (in the supervised learning setting) or encode some action (in the reinforcement learning setting).
\paragraph{Controller}
This input is passed to the controller network, alongside the contents of each of the read heads as drawn from the memory at the previous time instance: $\pmb{r}_{t-1}^{i},\ i \in 1, \dots ,R$. The concatenation of the above yields a vector $\pmb{\chi}_t \in \mathbb{R}^{X + RW}: \pmb{\chi}_t = [\pmb{x}_t; \pmb{r}_{t-1}^1; \dots \pmb{r}_{t-1}^R ] $. A full sequence of such inputs, $[\pmb{\chi}_1,\dots ,\pmb{\chi}_T]$ is passed through a set of dynamic state equations $\mathcal{N}$, as implemented by the controller, that yield back two intermediate outputs, $\pmb{\upsilon }_T$ and $\pmb{\xi}_T$, such that $\mathcal{N}([\pmb{\chi}_1,\dots,\pmb{\chi}_T]) = (\pmb{\upsilon}_T,\ \pmb{\xi}_T)$. The exact implementation of $\mathcal{N}$ is not essential to the architecture as a whole; $\mathcal{N}$ may be any neural network. Deep long short-term memory networks are the state of the art in sequential modeling, and therefore make for a reasonable choice, since the controller needs to be expressive enough to handle potentially complex data streams.

Out of the vectors $(\pmb{\upsilon}_t,\ \pmb{\xi}_t)$ returned by the controller, the first corresponds to the intermediate user-level output. Before conveying this to the user, the system is allowed one last peak at the memory. This is necessitated by the fact that the read head contents at the final timestep of the computation cannot be used in $\mathcal{N}$, as this would introduce circular dependencies in the architecture's computational graph. The memory conditioning process is therefore done outside the controller, as captured by a simple trainable linear map \begin{equation}
\notag
\pmb{y}_t = \pmb{\upsilon}_t + \pmb{W}_R[\pmb{r}_{t}^1;\dots;\pmb{r}_{t}^R]
\label{eqn:Memory Conditioning}
\end{equation}
The result of the operation is the current instance of the user-level output stream, $\pmb{y}_t$, which represents what the DNC is yielding back to the world while computing.

The second controller output, $\pmb{\xi}_t$, corresponds to the \textbf{interface vector}, which defines the controller's interaction with the memory. The interface vector can be subvidided into multiple smaller components, each one of which is responsible for a specific subtask related to memory adressing. Different activation functions are applied to these components, so as to enforce their distributions to fall within their task-specific domain. Post activation application, we have the following vectors and scalars:

\vspace{10pt}
\hspace{-40pt}
\begin{minipage}{0.6\textwidth}
\begin{itemize}
\item Read keys: \{$\pmb{k}_t^{r,i} \ \in \mathbb{R}^W, \ \forall i \in \{1,\dots,R\}$\}
\item Read strengths: \{$\beta_t^{r,i} \ \in [1, \infty) \ \forall i \in \{1,\dots,R\}$\}
\item Write key: $\pmb{k}_t^w \ \in \mathbb{R}^W$
\item Write strength: $\beta_t^w \ \in [1, \infty)$
\item Erase vector: $\pmb{e}_t \ \in [0,1]^W$
\end{itemize}
\end{minipage}
\hspace{-20pt}
\begin{minipage}{0.5\textwidth}
\begin{itemize}
\item Write vector: $\pmb{v}_t \ \in \mathbb{R}^W$
\item R free gates: \{$f_t^i \ \in [0,1] \ \forall i \in \{1,\dots,R\}$\}
\item Allocation gate: $g_t^a \ \in [0,1]$
\item Write gate: $g_t^w \ \in [0,1]$
\item Read modes: \{$\pmb{\pi}_t^i \ \in \mathcal{S}^3 \ \forall i \in \{1,\dots,R\}$\}
\end{itemize}
\end{minipage}
\vspace{10pt}

The remainder of this section is dedicated to examining the role of each of these components.

\paragraph{Content-based Addressing} 
DNCs perform content-based addressing via \textbf{autoassociative memory}. Autoassociative memory is a strong mechanism of content-lookup, that allows a system to navigate rich data structures and selectively retrieve relevant memory objects when only shown parts thereof. The implementation involves a \textit{matching function} $\mathcal{D}: \mathbb{R}^W \times \mathbb{R}^W \to \mathbb{R}$, which is applied on a read/write key $\pmb{k}$, as given by the controller, and the contents of a memory address, $\pmb{M}[i,:]$, and returns a scalar indicating how similar these two are. Any metric of distance may be used as $\mathcal{D}$, but the most obvious choice is cosine similarity:
 \[
 \tag{Cosine Similarity}
\mathcal{D}(\pmb{x}, \pmb{y}) = cos(\pmb{x},\pmb{y}) = \frac{\pmb{x} \cdot \pmb{y}}{||\pmb{x}|| \cdot ||\pmb{y}||}
\]
The controller may assign varying relative importance on different keys; this is accomplished by exponentially scaling the matches obtained by $\mathcal{D}$, using the strength vector associated with each key. These weighted matches are finally normalized by their sum, constraining the results within $\mathcal{S}^N$. The above are captured by a \textit{weighting function} $\mathcal{C}: \mathbb{R}^{N \times W} \times \mathbb{R}^W \times \mathbb{R} \to \mathbb{R}^N$, such that:
\[
\tag{Weighting Function}
\mathcal{C}(\pmb{M},\pmb{k}, \beta)[i] = 
\frac{ \mathcal{D}(\pmb{M}[i,:],\pmb{k})^{\beta} }
{\sum\nolimits_{j=1}^N \mathcal{D}(\pmb{M}[j,:],\pmb{k})^{\beta}}
\]

This is a fully differentiable form of attention, which allows the controller to construct minimal representations of objects that it's looking for in the memory. The key benefit of such a process is its ability to perform partial matching or pattern completion; for instance, the controller may simply construct the beginning of a sequence (e.g. the identifier of a variable), and, upon finding its match, it can then retrieve the full sequence (e.g. the  value of that variable) back from the memory.

The weighting function is used to obtain content-based weightings for both the read heads, denoted by $[\pmb{w}_t^{r,i},\dots,\pmb{w}_t^{r,R}]$, and the the write head, $\pmb{w}_t^w$. Given such weightings, a read head will contain a weighted average of the memory matrix:
\[
\tag{Memory Reading}
\pmb{r}_t^i = \pmb{M}_t^{\top} \pmb{w}_t^{r,i} 
\]
Writing to the memory is also dictated by a similar operation, which must now be defined via a recurrency relation to take into account past memory contents as well as the erase and write vectors emitted by the controller:
\[
\tag{Memory Writing}
\pmb{M}_t = \underbrace{\pmb{M}_{t-1} \circ (\pmb{1} - \pmb{w}_t^w \pmb{e}_t^\top)}_{\text{\scriptsize Partially erased past memory}} + \underbrace{\pmb{w}_t^w \pmb{v}_t^\top}_{\text{\scriptsize New memory}}
\]

\paragraph{Dynamic Allocation} Memory management is an integral part of any computer program. The DNC needs to be able to allocate and deallocate memory dynamically, according to the current execution's needs. This is achieved through a differentiable variation of the \textit{free-list scheme}. In its original form, the free-list scheme allows a system to keep track of unused memory blocks by connencting them with one another as a linked-list. Its adaptation for the purposes of the DNC is slightly more involved, as described next. Before writing to the memory, the controller emits a free gate, $f_t^i$, for each read head $i$, which controls to what extend a recently read memory address may be deallocated. From the latter , the \textit{retention vector} can be obtained as:
\[
\tag{Retention Vector}
\pmb{\psi}_t = \prod\limits_{i=1}^{R}{(\pmb{1}-f_t^i \pmb{w}_t^{r,i})}
\]

The retention vector is a measure of how much each memory address needs to be retained. Its complement, the \textit{usage-tracking vector} $\pmb{u}_t$, annotates each memory address with a scalar so to as to signal how strongly it is being used. It is recursively defined as follows:
\[
\tag{Usage-tracking Vector}
\pmb{u}_t = \underbrace{(\pmb{u}_{t-1} + \pmb{w}_{t}^{w} - \pmb{u}_{t-1} \circ \pmb{w}_t^{w})}_{\text{ \scriptsize Previous usage OR New write}} \circ \ \pmb{\psi}_t
\]
Contrary to first impressions, the above equation is quite intuitive. The parenthesized term sums the previous usage tracking vector with the current write weighting minus their dot product, acting as a real-valued variation of the logical OR function. A single element of this term, $\pmb{u}_t[i]$ would denote the pre-retention usage tracking of memory address $i$; it is close to $1$ if was either already in use, or just written to. Multiplied by its corresponding element of the retention vector, it can then be (partially) deallocated.

Finally, the free-list $\pmb{\phi}_t$ is defined as the sorted list of indices of the usage-tracking vector, i.e. $\pmb{\phi}_t[i]$ is the index of the i-th least used address in the memory. The \textit{allocation vector} $\pmb{a}_t$ is then  used to annotate the availability of each memory address:
\[
\tag{Allocation Vector}
\label{eqn:Allocation Vector}
\pmb{a}_t[\pmb{\phi}_t[j]] = (1 - \pmb{u}_t[\pmb{\phi}_t[j]])\prod\limits_{i=1}^{j-1}{\pmb{u}_t[\pmb{\phi}_t[i]]} \ \in [0,1]
\]

To showcase the functionality of this last equation, we will consider a simple example. Let $\pmb{u}_t = [0.4, 0.8, 0.1]$ be the usage-tracking vector of a 3-address memory at timestep $t$. Then the free-list would be $\pmb{\phi}_t = [3, 1, 2]$. Iterating over \ref{eqn:Allocation Vector} we then get:
\begin{align*}
\pmb{a}_t[\pmb{\phi}_t[1]] &= \pmb{a}_t[3] = (1-\pmb{u}_t[3]) \cdot 1 = (1-0.1) =0.9 \\
\pmb{a}_t[\pmb{\phi}_t[2]] &= \pmb{a}_t[1] = (1-\pmb{u}_t[1]) \cdot \pmb{u}_t[3] = (1 - 0.4) \cdot 0.1 = 0.06\\
\pmb{a}_t[\pmb{\phi}_t[3]] &= \pmb{a}_t[2] = (1-\pmb{u}_t[2]) \cdot \pmb{u}_t[3] \cdot \pmb{u}_t[1] = (1-0.8) \cdot 0.1 \cdot 0.4 = 0.008
\end{align*}
Therefore $\pmb{a}_t = [0.06, 0.08, 0.9]$.

Having the allocation vector, the controller can now shift its attention towards unused memory addresses using the allocation gate $g_t^a$. The shifted weightings are then gated by the write gate $g_t^w$, which acts as a memory-locking mechanism :
\[
\tag{Allocation Shift}
\underbrace{\pmb{w}_t^w}_{\text{\scriptsize Updated weights}} = \underbrace{g_t^w}_{\text{Write-lock}} \quad [ \hspace{-10pt} \underbrace{g_t^a \pmb{a}_t}_{\text{\scriptsize Shifted weights}} + \underbrace{(1-g_t^w) \ \pmb{w}_t^w}_{\text{\scriptsize Writeable original weights}} \hspace{-15pt}]
\]

\paragraph{Temporal Linking} One last mechanism of memory addressing employed by DNCs is temporal linking. Temporal linking is necessary in order to perform sequential retrieval, when sequences are stored in disparate, non-contiguous blocks. The key-element of the process is a temporal transition matrix $\pmb{L} \in [0,1]^{N\times N}$, which keeps track of the temporal order by which memory addresses have been written to. More conretely, $\pmb{L}[i,j]$ is close to $1$ if $j$ was strongly written to after $i$, or close to $0$ otherwise. $\pmb{L}$ is again defined via a recurrency relation; a slightly simplified version of the one in the original paper is presented below, for the sake of brevity and clarity.
\[
\tag{Temporal Update}
\pmb{L}[i,j] = \underbrace{(1 - \pmb{w}_t^w[i] - \pmb{w}_t^w[j]) \pmb{L}_{t-1}[i,j]}_{\text{\scriptsize Part of last transition}} + \underbrace{\pmb{w}_{t-1}^w[i] \pmb{w}_{t}^w[j]}_{\text{\scriptsize New transition}}
\]
The above equation is also quite intuitive. The first term of the addition allows the transition value between $i$ and $j$ to propagate through time. The old transition, $\pmb{L}_{t-1}[i,j]$ is complentary to the amount of writing performed in these addresses; even if we had a transition in the past, it no longer holds if either $i$ or $j$ were just written to. On the other hand, if $i$ was written to in the previous timestep and $j$ was written to in the current timestep, then a new transition is instantiated. This is captured by the second term of the addition.

\paragraph{Mode Interpolation} The temporal transition matrix can be used as another means of attention; this time, the controller can shift its attention over the memory through time. $\pmb{L}_t \pmb{w}$ shifts the weightings $\pmb{w}$ forwards in time, whereas $\pmb{L}_t^\top \pmb{w}$ shifts them backwards. The degree to which the controller performs forward, backward, or no temporal iteration is dictated by the read modes $\pmb{\pi}_t^i$ for each read head $i$:
\[
\tag{Temporal Shift}
\pmb{w}_t^{r,i} = 
\underbrace{\pmb{\pi}_t^i[1] \pmb{L}_t\pmb{w}_t^{r,i}}_{\text{\scriptsize Forward shift}} + 
\underbrace{\pmb{\pi}_t^i[2] \pmb{w}_t^{r,i}}_{\text{\scriptsize No shift}} + 
\underbrace{\pmb{\pi}_t^i[3] \pmb{L}_t^\top \pmb{w}_t^{r,i}}_{\text{\scriptsize Backward shift}}
\]

\section{Conclusion}

\end{document}

### 2018-06-04 Paper/Paper.tex
up to 1-layer case

@@
 \paragraph{Controller}
-This input is passed to the controller network, alongside the contents of each of the read heads as drawn from the memory at the previous time instance: $\pmb{r}_{t-1}^{i},\ i \in 1, \dots ,R$.
+The aforementioned input is passed to the controller network, alongside the contents of each of the read heads as drawn from the memory at the previous time instance: $\pmb{r}_{t-1}^{i},\ i \in 1, \dots ,R$.
 The concatenation of the above yields a vector $\pmb{\chi}_t \in \mathbb{R}^{X + RW}: \pmb{\chi}_t = [\pmb{x}_t; \pmb{r}_{t-1}^1; \dots \pmb{r}_{t-1}^R ] $.
@@
 
-The second controller output, $\pmb{\xi}_t$, corresponds to the \textbf{interface vector}, which defines the controller's interaction with the memory.
+The second controller output, $\pmb{\xi}_t$, corresponds to the \textit{interface vector}, which defines the controller's interaction with the memory.
 The interface vector can be subvidided into multiple smaller components, each one of which is responsible for a specific subtask related to memory adressing.
@@
 \paragraph{Content-based Addressing} 
-DNCs perform content-based addressing via \textbf{autoassociative memory}.
+DNCs perform content-based addressing via \textit{autoassociative memory}.
 Autoassociative memory is a strong mechanism of content-lookup, that allows a system to navigate rich data structures and selectively retrieve relevant memory objects when only shown parts thereof.
@@
  \[
- \tag{Cosine Similarity}
+ \tag{Cosine Similarity} \label{eqn:Cosine}
 \mathcal{D}(\pmb{x}, \pmb{y}) = cos(\pmb{x},\pmb{y}) = \frac{\pmb{x} \cdot \pmb{y}}{||\pmb{x}|| \cdot ||\pmb{y}||}
@@
 The parenthesized term sums the previous usage tracking vector with the current write weighting minus their dot product, acting as a real-valued variation of the logical OR function.
-A single element of this term, $\pmb{u}_t[i]$ would denote the pre-retention usage tracking of memory address $i$; it is close to $1$ if was either already in use, or just written to.
+A single element of this term, $\pmb{u}_t[i]$ would denote the pre-retention usage tracking of memory address $i$; it is close to $1$ if it was either already in use, or just written to.
 Multiplied by its corresponding element of the retention vector, it can then be (partially) deallocated.
@@
 The first term of the addition allows the transition value between $i$ and $j$ to propagate through time.
-The old transition, $\pmb{L}_{t-1}[i,j]$ is complentary to the amount of writing performed in these addresses; even if we had a transition in the past, it no longer holds if either $i$ or $j$ were just written to.
+The extend of propagation of the old transition, $\pmb{L}_{t-1}[i,j]$, is complentary to the amount of writing performed in these addresses; even if we had a transition in the past, it no longer holds if either $i$ or $j$ were just written to.
 On the other hand, if $i$ was written to in the previous timestep and $j$ was written to in the current timestep, then a new transition is instantiated.
@@
 
-\paragraph{Mode Interpolation} The temporal transition matrix can be used as another means of attention; this time, the controller can shift its attention over the memory through time.
+\paragraph{Mode Interpolation} The temporal transition matrix can be used as one last means of attention; simply multiplying the matrix by a weighting vector allows the controller to shift its attention over the memory, now through time.
 $\pmb{L}_t \pmb{w}$ shifts the weightings $\pmb{w}$ forwards in time, whereas $\pmb{L}_t^\top \pmb{w}$ shifts them backwards.
-The degree to which the controller performs forward, backward, or no temporal iteration is dictated by the read modes $\pmb{\pi}_t^i$ for each read head $i$:
+The degree to which the controller performs forward, backward, or no temporal iteration is dictated by the read modes $\pmb{\pi}_t^i$ emitted by the controller for each read head $i$:
 \[
 \tag{Temporal Shift}
-\pmb{w}_t^{r,i} = 
+\underbrace{\pmb{w}_t^{r,i}}_{\text{\scriptsize Updated weights}} \hspace{-10pt} = \quad
 \underbrace{\pmb{\pi}_t^i[1] \pmb{L}_t\pmb{w}_t^{r,i}}_{\text{\scriptsize Forward shift}} + 
@@
 
+\section{End-to-End Memory Networks}
+\subsection{Description}
+An end-to-end memory network is a neural architecture that also connects a RNN with a large memory array.
+The external nature of this array is disanalogous to traditional architectures, such as the LSTM, where the memory is encapsulated within the neural layers.
+Under this perspective, it can be seen as true long-term memory.
+The memory can be read from (potentially multiple times) during computation, using a straightforward attentional layer; the architecture therefore benefits from context-sensitive addressing capabilities.
+The overall model is simple, yet efficient, and includes no discontinuities in its operations, thus being trainable with gradient-based methods.
+
+\subsection{Architecture}
+\paragraph{Overview}
+An end-to-end memory network receives two inputs; a sequence of vectors $\{\pmb{x}_1,\dots,\pmb{x}_N\}$ and a query $\pmb{q}$.
+Both $\pmb{x}_i$ and $\pmb{q}$ are defined as symbols originating from a vocabulary $\mathcal{V}$.
+The network processes these inputs to return an answer $\pmb{a}$.
+This output is produced by first constructing continuous representations for both the input sequence and the query, and then iterating over these representations in many \textit{hops}, i.e.
+computational steps.
+The authors treat two different cases of this process; the first and simplest one employing a single layer, and the second, more general one, employing multiple layers.
+As this approach is favorable for understanding the architecture, we are also going to follow along the same route, modulo a few minor alterations and clarifications.
+
+\paragraph{Single-Layer Case} First, note that a symbol $x$ from a strictly total-ordered vocabulary $\mathcal{V}$ can be represented as a vector $\pmb{x} \in \mathbb{R}^{V}$, where $V = ||\mathcal{V}||$ the size of the vocabulary.
+This is often referred to as \textit{one-hot encoding}.
+Given a character $x$ that coincides with the i-th element of $\mathcal{V}$, one-hot encoding is achieved by mapping $x$ to a vector $\pmb{x}$ whose elements are all $0$, except the $i$-th element which is $1$.
+This is the assumed form of input representation for the sequence $\{\pmb{x}_i\}$ and the query $\pmb{q}$.
+
+The above are transformed into two new, continuous spaces of dimensionality $d$; from each input $\pmb{x}_i$ we get a memory object $\pmb{m}_i$, whereas the query $\pmb{q}$ becomes an internal representation $\pmb{u}$.
+The transformations may be the result of any trainable operation, with the easiest choice being two \textit{embedding matrices} $\pmb{A}, \pmb{B} \in \mathbb{R}^{d\times V}$, such that:
+\begin{align}
+\pmb{m}_i &= \pmb{A}\pmb{x}_i \tag{Memory Transformation} \\
+\pmb{u} &= \pmb{B}\pmb{q} \tag{Query Transformation}
+\end{align}
+
+As soon as we obtain the above, the matching vector $\pmb{p}$ between the query transformation and each memory object can be computed by passing the product of the two, $\pmb{u}^\top \pmb{m}_i$, through a Softmax activation:
+\[
+\tag{Memory Matching}
+\pmb{p}_i = Softmax(\pmb{u}^\top \cdot \pmb{m}_i) = \frac{e^{\pmb{u}^\top\pmb{m}_i}}{\sum_j{e^{\pmb{u}^\top\pmb{m}_j}}}
+\]
+The inner product can be seen as a measure of similarity (reminiscent of \ref{eqn:Cosine}, minus the normalization), and the softmax activation is used to constrain $\pmb{p}$ within $\mathcal{S}^N$.
+
+A third transformation, via a third embedding matrix $\pmb{C} \in \mathbb{R}^{d\times V}$, is used to map inputs $\{\pmb{x}_i\}$ to their output representations $\{\pmb{c}_i\}$, from which the memory response can be derived as their match-weighted sum:
+\begin{align}
+\tag{Output Transformation}
+\pmb{c}_i &= \pmb{C}\pmb{x}_i\\
+\tag{Memory Response}
+\pmb{o} &= \sum\limits_i{\pmb{p}_i\pmb{c}_i}
+\end{align}
+
+The ingenuity of this last equation is perhaps masked by its simplicity.
+It essentially accounts for a form of soft attention; the query dictates which parts of the output representation to focus on, depending on how it matched with the input representation.
+In other words, even though we always get the same output representation sequence $\{\pmb{c}_i\}$ from an input sequence $\{\pmb{x}_i\}$, the query $\pmb{q}$ plays an important role on how the network utilizes it.
+
+Finally, the memory response is combined with the query representation through some binary operation (e.g.
+concatenation, element-wise addition or multiplication, etc.) and is passed through one last layer responsible for the final prediction.
+In the original paper, which assumes a classification setting, the authors propose a Softmax-activated linear map over the addition of the query and the response:
+\[
+\tag{Final Prediction}
+\hat{\pmb{a}} = Softmax(\pmb{W} (\pmb{o}+\pmb{u}))
+\]
+
+Of course, this may be altered according to the requirements and restrictions imposed by the particular experimental environment.
+
+\paragraph{Multi-Layer Case}
+
+\section{Comparison}
+
 \section{Conclusion}

### 2018-06-13 Paper/Paper.tex
minor

@@
 
-A particularly interesting subclass of neural networks are \textit{Recurrent Neural Networks} (RNNs).
-Unlike traditional networks, which accept a fixed-size input vector and produce a fixed-size output vector over a finite number of computational steps, RNNs instead operate on sequences of vectors.
-This additional axis is captured by allowing the RNN to accept one vector at a time and construct an intermediate representation of it, which then combines with the next input vector to affect the computation of the next such representation (Fig.\ref{fig:1}).
+A particularly interesting class of neural networks are \textit{Recurrent Neural Networks} (RNNs).
+Unlike fully-connected networks, which accept a fixed-size input vector and produce a fixed-size output vector over a finite number of computational steps, RNNs instead operate on sequences of vectors.
+This additional axis of dependencies is captured by a recurrency relation interlinking the network's hidden states through time.
+More concretely, the hidden representation is no longer conditioned on just the current input, but also on the immediately previous version of itself (Fig.\ref{fig:1}).
 This elegant addition accounts for a drastic improvement in the representational capacity of the network.
-Whereas a simple net acts as a fixed function, a RNN acts as a program operating on sequences of inputs.
+Whereas a simple net acts as a trainable (but parametrically fixed) function, a RNN acts as a continuous program operating on sequences of inputs.
 Under this viewpoint, the RNN's hidden representation can be perceived as the program's internal variables, updating as new inputs are received and affecting the computation as it progresses.
@@
 Their ability to model sequential patterns and their interesting properties have garnered a lot of attention, yet they still suffer from two major drawbacks.
-The first relates to the statefulness achieved by their intermediate representation; even though it is distributed, the hidden vector's size is finite and fixed, therefore capable of only limited, lossy storage.
+The first relates to the statefulness achieved by their intermediate representation; even though it is distributed (hence more expressive than stochastic FSAs or Markov models), the hidden vector's size is finite and fixed, therefore capable of only limited, lossy storage.
 The second is a more intrinsic one and is not only tied to RNNs but neural networks in general; there is no separation between memory and processing, as each neuron is simultaneously a minimal storage unit and a computational one.
@@
 A series of advancements has seeked to enhance RNNs with stronger memory management.
-Starting with the introduction of the \textit{Long Short-Term Memory}, which permits finite storage over arbitrary long computations, research in RNNs has bloomed towards many different directions.
+Starting with the introduction of the \textit{Long Short-Term Memory}, which permits finite storage over very long computations, research in RNNs has bloomed towards many different directions.
 One particularly exciting recent advancement is the so-called \textit{attentional interface}, which allows a network to selectively shift its focus on particular indices over a set of dimensions of an arbitrary tensor, thus enabling content-based adressing.
@@
 \paragraph{Overview} 
-A differentiable neural computer consists of two main components; a recurrent neural network \textbf{controller network} and an external \textbf{memory matrix} $M \in \mathbb{R}^{N\times W}$.
+A differentiable neural computer consists of two main components; a recurrent neural network, called the \textbf{controller network}, and an external \textbf{memory matrix} $M \in \mathbb{R}^{N\times W}$.
 The matrix contains $N$ memory adresses, each of size $W$, which can be read by the controller through $R$ \textit{read heads}, or written to by one \textit{write head}.
@@
 The interface vector can be subvidided into multiple smaller components, each one of which is responsible for a specific subtask related to memory adressing.
-Different activation functions are applied to these components, so as to enforce their distributions to fall within their task-specific domain.
+Different activation functions are applied to these components, forcing their distributions to lie within the domain dictated by their specific task.
 Post activation application, we have the following vectors and scalars:
@@
 \]
-The controller may assign varying relative importance on different keys; this is accomplished by exponentially scaling the matches obtained by $\mathcal{D}$, using the strength vector associated with each key.
+The controller may assign varying relative importance on different keys; this is accomplished by raising the matches obtained by $\mathcal{D}$ to the strength vector associated with each key.
 These weighted matches are finally normalized by their sum, constraining the results within $\mathcal{S}^N$.
@@
 Before writing to the memory, the controller emits a free gate, $f_t^i$, for each read head $i$, which controls to what extend a recently read memory address may be deallocated.
-From the latter , the \textit{retention vector} can be obtained as:
+From the latter, the \textit{retention vector} can be obtained as:
 \[
@@
 The retention vector is a measure of how much each memory address needs to be retained.
-Its complement, the \textit{usage-tracking vector} $\pmb{u}_t$, annotates each memory address with a scalar so to as to signal how strongly it is being used.
+Its functional complement, the \textit{usage-tracking vector} $\pmb{u}_t$, annotates each memory address with a scalar, responsible for signaling how strongly it is being used.
 It is recursively defined as follows:

### 2018-06-14 Paper/Paper.tex
meh

@@
 \usepackage{subcaption}
+\usetikzlibrary{calc, trees, fit, positioning}
 
@@
 tasks requiring data storage and retrieval, have however proven difficult for neural networks to model.
-This paper serves as a literature review of two recent approaches towards bypassing this limitation, namely Differentiable Neural Computers (DNCs) and End-to-End Memory Networks.
-The rest of this section will briefly introduce some important background concepts, before the models' details are examined in sections 2 and 3, respectively.
-Section 4 provides a short discussion and a comparative analysis on the two approaches, and section 5 presents some concluding remarks.
+This paper serves as a literature review of two recent approaches towards bypassing this limitation, namely Differentiable Neural Computers\cite{Graves2016} and End-to-End Memory Networks\cite{NIPS2015_5846}.
+The rest of this section will briefly introduce some important background concepts, before some notation is established in Section \ref{sec:Notation}.
+The models' details are examined in Sections \ref{DNC} and \ref{E2E}, respectively.
+Section \ref{Comp} provides a short discussion and a comparative analysis on the two approaches, and Section \ref{Conc} presents some concluding remarks.
 
@@
 This elegant addition accounts for a drastic improvement in the representational capacity of the network.
-Whereas a simple net acts as a trainable (but parametrically fixed) function, a RNN acts as a continuous program operating on sequences of inputs.
+Whereas a simple net acts as a trainable (but parametrically fixed) function, a RNN acts as a continuous program operating on sequences of inputs, and is in fact Turing complete\cite{Siegelmann545}.
 Under this viewpoint, the RNN's hidden representation can be perceived as the program's internal variables, updating as new inputs are received and affecting the computation as it progresses.
 
-\begin{figure}[h!]
+\begin{figure}
 \begin{minipage}{0.5\textwidth}
@@
 	\begin{tikzpicture}[scale=0.5]
+		\node (X) at (-1, -2) {$\pmb{x}$};
 		\foreach \y /\alph/\name in {
-			0/x1/$x_1$,
-		  	-1/x2/$x_2$,
-		  	-2/x3/$x_3$,
-		  	-4/xM/$x_M$
+			0/x1/{},
+		  	-1/x2/{},
+		  	-2/x3/{},
+		  	-4/xM/{}
 		 }{
-		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{black}{\name}};
+		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=4mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{black}{\name}};
 		 }
+		 \node (H) at (4, 2.5) {$\pmb{h}$};
 		 \node (x..) at (0,-3) {\tiny {\vdots}};
 		 \foreach \y /\alph/\name in {
-			1/h1/$h_1$,
-		  	0/h2/$h_2$,
-		  	-1/h3/$h_3$,
-		  	-5/hN/$h_N$
+			1.5/h1/{},
+		  	0/h2/{},
+		  	-1.5/h3/{},
+		  	-5.5/hN/{}
 		 }{
@@
 		 \node (h..) at (4,-3) {\tiny {\vdots}};
+		 \node (Y) at (9, -2) {$\pmb{y}$};
 		 \foreach \y /\alph/\name in {
-			0/y1/$y_1$,
-		  	-1/y2/$y_2$,
-		  	-2/y3/$y_3$,
-		  	-4/yP/$y_P$
+			0/y1/{},
+		  	-1/y2/{},
+		  	-2/y3/{},
+		  	-4/yP/{}
 		 }{
@@
 	\begin{tikzpicture}[scale=.5]
+		\node (X) at (-1, -2) {$\pmb{x}$};
 		\foreach \y /\alph/\name in {
-			0/x1/$x_1$,
-		  	-1/x2/$x_2$,
-		  	-2/x3/$x_3$,
-		  	-4/xM/$x_M$
+			0/x1/{},
+		  	-1/x2/{},
+		  	-2/x3/{},
+		  	-4/xM/{}
 		 }{
@@
 		 \node (x..) at (0,-3) {\tiny {\vdots}};
+	  \node (H) at (4, 2.5) {$\pmb{h}$};
 		 \foreach \y /\alph/\name in {
-			1/h1/$h_1$,
-		  	0/h2/$h_2$,
-		  	-1/h3/$h_3$,
-		  	-5/hN/$h_N$
+			1.5/h1/{},
+		  	0/h2/{},
+		  	-1.5/h3/{},
+		  	-6.5/hN/{}
 		 }{
@@
 	\end{minipage}
-	\caption[Hello world]
-	{\small \textit{Comparison between a simple neural network and a RNN.
+	\caption[]
+	{\small \textit{Comparison between a feedforward neural network and a RNN.
 (a) The simple network applies two transformations $\pmb{x} \mapsto \pmb{h}$ and $\pmb{h} \mapsto \pmb{y}$, the composition of which can be seen as a function $\pmb{x} \mapsto \pmb{y}$.
@@
 Their ability to model sequential patterns and their interesting properties have garnered a lot of attention, yet they still suffer from two major drawbacks.
-The first relates to the statefulness achieved by their intermediate representation; even though it is distributed (hence more expressive than stochastic FSAs or Markov models), the hidden vector's size is finite and fixed, therefore capable of only limited, lossy storage.
+The first relates to the statefulness achieved by their intermediate representation; even though it is distributed (hence more expressive than stochastic FSAs or Markov models)\cite[Lecture~10]{Hinton13}, the hidden vector's size is finite and fixed, therefore capable of only limited, lossy storage.
 The second is a more intrinsic one and is not only tied to RNNs but neural networks in general; there is no separation between memory and processing, as each neuron is simultaneously a minimal storage unit and a computational one.
-Although appealing from a biological perspective, this goes against the von Neumann model and our programming paradigm.
+Although appealing from a biological perspective, this goes against the von Neumann model and the modern programming paradigm.
 
 A series of advancements has seeked to enhance RNNs with stronger memory management.
-Starting with the introduction of the \textit{Long Short-Term Memory}, which permits finite storage over very long computations, research in RNNs has bloomed towards many different directions.
-One particularly exciting recent advancement is the so-called \textit{attentional interface}, which allows a network to selectively shift its focus on particular indices over a set of dimensions of an arbitrary tensor, thus enabling content-based adressing.
+Starting with the introduction of the \textit{Long Short-Term Memory}\cite{Hochreiter:1997:LSM:1246443.1246450,Gers99learningto}, which permits finite storage over very long computations, research in RNNs has bloomed towards many different directions.
+One particularly exciting recent advancement is the so-called \textit{attentional interface}\cite{NIPS2014_5542,Bahdanau} (Fig.\ref{fig:2}), which allows a network to selectively shift its focus on particular indices over a set of dimensions of an arbitrary tensor, thus enabling content-based adressing.
 The implications of this seemingly simple trick are tremendous; when employing fully differentiable attention (soft-attention), a network can learn how to pick out and combine relevant elements out of a (potentially very large) tensor, instead of lossily encoding it.
-This translates to arbitrary information retrieval; in other words, the same representations can now have different effects on the computation depending on the present context, similar to how a computer program would refer only to the variables dictated by its currently run instruction.
-Since its inception, attention has been a key-concept in many influential publication; the creative liberty it is offering, in terms of new potential operations, has also paved the way for architectures which decouple storage from computation.
+This translates to arbitrary information retrieval; in other words, the same representations can now have different effects on the computation depending on the present context, similar to how a computer program would refer only to the variables dictated by its currently run instruction\cite{NIPS2014_5346}.
+Since its inception, attention has been a key-concept in many influential publications; the creative liberty it is offering, in terms of new potential operations, has also paved the way for architectures which decouple storage from computation.
 Such architectures, including but not limited to the two presented in this paper, utilize large external matrices and employ attention to perform read and write operations on them.
 
+\begin{figure}
+	\centering
+	\begin{tikzpicture}
+		[auto,
+		scale=0.65,
+		h/.style = {draw=black, rectangle, text centered, text depth=0.5em, text width = 2em, text height=1em,  align=center},
+		c/.style = {draw=black, circle, minimum size=1mm, inner sep=0pt},
+		c2/.style = {draw=black, circle, minimum size=2mm, inner sep=0pt}]
+
+		\node (alpha) at (-2, 5.5) {$a$};
+		\foreach \y/\alph in {
+			4/Nx1,
+			3.25/Nx2,
+			2.5/Nx3}{
+			\node[c2] (\alph) at (-3,\y) {};
+		}
+		\foreach \y/\alph in {
+			4.75/Nh1,
+			4/Nh2,
+			3.25/Nh3,
+			2.5/Nh4,
+			1.75/Nh5}{
+			\node[c2] (\alph) at (-2,\y) {};
+		}
+		\foreach \y/\alph in {
+			4/Ny1,
+			3.25/Ny2,
+			2.5/Ny3}{
+			\node[c2] (\alph) at (-1,\y) {};
+		}
+
+		\foreach \source in {Nx1, Nx2, Nx3}{
+		\foreach \target in {Nh1, Nh2, Nh3, Nh4, Nh5}{
+			\draw (\source) edge (\target);}}
+		\foreach \source in {Nh1, Nh2, Nh3, Nh4, Nh5}{
+		\foreach \target in {Ny1, Ny2, Ny3}{
+			\draw (\source) edge (\target);}}
+
+		\node (h..) at (5.25,0) {$\dots$};
+		\foreach \x/\alph/\name in {
+			0/h1/$\pmb{h}_1$,
+			2.5/h2/$\pmb{h}_2$,
+			8/hT/$\pmb{h}_T$
+		}{
+			\node[h] (\alph) at (\x,0) {\name};
+		}
+		\node[h] (c) at (4,5) {$\pmb{c}$};
+
+		\node[c] (+) at (4, 3) {$+$};
+
+		\node[c] (x1) at (1.65,1.5) {\small $\times$};
+		\node[c] (x2) at (3.05,1.5) {\small $\times$};
+		\node[c] (xT) at (6.35,1.5) {\small $\times$};
+
+		\draw (0,-1.5) edge[dashed] (h1);	
+		\draw (2.5,-1.5) edge[dashed] (h2);	
+		\draw (8,-1.5) edge[dashed] (hT);	
+		\draw (h1.north) edge (x1);
+		\draw (x1) edge (+);
+		\draw (h2.north) edge (x2);
+		\draw (x2) edge (+);
+		\draw (hT.north) edge (xT);
+		\draw (xT) edge (+);
+		\draw (+) edge[->] (c);
+
+		\draw (-4,4) edge[dashed] (Nx1);
+		\draw (-4,3.25) edge[dashed] (Nx2);
+		\draw (-4,2.5) edge[dashed] (Nx3);
+
+		\draw (Ny1)  [dashed] .. controls +(0.8,0.8) and +(-0.8,0.8) ..  (x1);
+		\draw (Ny2)  [dashed] .. controls +(3,3) and +(-0.6,0.6) ..  (x2);
+		\draw (Ny3)  [dashed] .. controls +(2,-3) and +(0.6,0.4) ..  (xT.west);
+	\end{tikzpicture}
+	\caption[]
+	{\small \textit{}\label{fig:2} General case of an attentional layer.
+Given some sequence $[\pmb{h}_1,\dots,\pmb{h}_T]$ (e.g.
+the hidden output of an RNN), we may use an neural function $a$ to obtain a weighting vector $\pmb{a} \in \mathbb{R}^{T}$.
+Multiplying each sequence element by its corresponding weight and summing up the results, we end up with a context vector $\pmb{c}$.
+Note that when $a$ accepts an external vector (or vector sequence) as its argument, the result is a context-dynamic selection of the $[\pmb{h}_1,\dots]$ sequence.}
+\end{figure}
+
 \section{Notation and Preliminaries}
+\label{sec:Notation}
 Given the technical nature of the works presented, it is important to establish a notational common ground.
@@
 \section{Differentiable Neural Computers}
+\label{DNC}
 \subsection{Description}
@@
 \paragraph{Content-based Addressing} 
-DNCs perform content-based addressing via \textit{autoassociative memory}.
+DNCs perform content-based addressing via \textit{autoassociative memory}\cite[Chapter~12]{rojas}.
 Autoassociative memory is a strong mechanism of content-lookup, that allows a system to navigate rich data structures and selectively retrieve relevant memory objects when only shown parts thereof.
@@
 Its functional complement, the \textit{usage-tracking vector} $\pmb{u}_t$, annotates each memory address with a scalar, responsible for signaling how strongly it is being used.
-It is recursively defined as follows:
+It is recurrently defined as follows:
 \[
@@
 \section{End-to-End Memory Networks}
+\label{E2E}
 \subsection{Description}
@@
 The external nature of this array is disanalogous to traditional architectures, such as the LSTM, where the memory is encapsulated within the neural layers.
-Under this perspective, it can be seen as true long-term memory.
+Considering this difference, it can be perceived as true long-term memory.
 The memory can be read from (potentially multiple times) during computation, using a straightforward attentional layer; the architecture therefore benefits from context-sensitive addressing capabilities.
@@
 
-\paragraph{Single-Layer Case} First, note that a symbol $x$ from a strictly total-ordered vocabulary $\mathcal{V}$ can be represented as a vector $\pmb{x} \in \mathbb{R}^{V}$, where $V = ||\mathcal{V}||$ the size of the vocabulary.
+\paragraph{Single-Layer Case} First, note that a symbol $x$ from a strictly total-ordered vocabulary $\mathcal{V}$ can be uniquely represented as a vector $\pmb{x} \in \mathbb{R}^{V}$, where $V = ||\mathcal{V}||$ the size of the vocabulary.
 This is often referred to as \textit{one-hot encoding}.
@@
 It essentially accounts for a form of soft attention; the query dictates which parts of the output representation to focus on, depending on how it matched with the input representation.
-In other words, even though we always get the same output representation sequence $\{\pmb{c}_i\}$ from an input sequence $\{\pmb{x}_i\}$, the query $\pmb{q}$ plays an important role on how the network utilizes it.
+In other words, even though we always get the same output representation sequence $\{\pmb{c}_i\}$ from some input sequence $\{\pmb{x}_i\}$, the query $\pmb{q}$ plays an important role on how the network utilizes it.
 
@@
 \paragraph{Multi-Layer Case}
+In the more general case, the network may consist of multiple stacked layers; the presence of $K$ memory layers would then translate to $K$ hops.
+The authors propose a few different variations of connections between the different layers, which are summarized below.
 
-\section{Comparison}
+The first layer would operate as described in the previous paragraph.
+For each layer after the first, its input is defined as a linear combination of the previous layer's query and output transformations, i.e.
+\[
+\tag{Next Query Transformation}
+\pmb{u}^{k+1} = \pmb{H}\pmb{u}^{k} + \pmb{o}^k 
+\]
+where $\pmb{H}$ may either be a trainable weight matrix (the same for all inter-layer links) or the identity matrix (in which case the query transformation is just added as is).
+
+Each layer applies the memory and output transformations on $pmb{x}$ with each own embedding matrices $A^k, C^k$.
+The authors, however, explore a few options of weight-sharing in order to reduce the parameter space.
+One such option is to follow the RNN paradigm, letting all matrices with the same functionality be the same:
+\[
+\tag{RNN-Tying}
+\forall \ (i,j): \pmb{A}^i = \pmb{A}^j, \pmb{C}^i = \pmb{C}^j
+\]
+This option is of particular interest, as then the network equations would be directly equivalent to those of RNNs, with one subtle but important difference.
+The intermediate representation $\pmb{p}$, which can be compared with the internal network recurrency, is not a static sample of the memory but rather a softly attended variant, which results in more expressive conditioning of the output on the memory.
+
+The other alternative proposed would be to tie these matrices in a way such that the memory representation of a layer is matched with the output representation of the previous one, in what the authors call adjacency tying.
+This can be achieved simply by letting:
+\[
+\tag{Adjacency Tying}
+\pmb{A}^{k+1} = \pmb{C}^k
+\]
+What this accomplishes is constructing output representations that are continuous and comparable to the input representations of the immediately next layer, facilitating easier training.
+
+\section{Discussion}
+\label{Comp}
+The previous sections have presented a summary of the design and functionality of two modern approaches towards enhancing recurrent networks with memory.
+This Section will be devoted to some commentary on what the implications of these networks are, how they compare to one another and what their relevance is to computation as a whole.
+
+\subsection{Comparisons}
+Whereas both models are improvements over traditional recurrent networks, they approach the problem from two entirely different angles.
+
+Differentiable Neural Computers present a concrete, well-thought architecture that can simulate traditional computation via purely differentiable operations.
+This is one of the very first instantations of a model that falls within the domain of \textit{Probabilistic Programming}\cite{Meijer}, an emerging programming paradigm that proposes treating computer programs as stochastic distributions.
+Examined end-to-end, Differentiable Neural Computers propose a system capable of learning task-specific memory management and computation.
+Its practical use cases may be limited, for the time being, but the contribution it makes as a whole is clear and rather groundbreaker; that of a single, unified machinery capable of learning programs with vastly different functionalities and input/output data structures.
+It is a huge leap towards automated program synthesis and recognition.
+At the same time, the authors pose strong arguments for their design decisions and draw parallels between biological intelligence and their system.
+
+Differentiable Neural Computers are the direct successor to Neural Turing Machines\cite{DBLP:journals/corr/GravesWD14}, a related architecture that has the same operative goals but slightly limited functions.
+More specifically, Neural Turing Machines lack the ability to perform temporal linking and dynamic memory allocation, both of which the Differential Neural Computers excel at.
+This in turn disabled them from performing iterative memory retrieval of sequences stored in remote blocks, and hindered their computational capacities at situations when reiterating through a previously used memory matrix.
 
 \section{Conclusion}
+\label{Conc}
+
+\bibliographystyle{ieeetr}
+\bibliography{sources}
 

### 2018-06-15 Paper/Paper.tex
draft

@@
 
-		\node[c] (x1) at (1.65,1.5) {\small $\times$};
+		\node[c] (x1) at (1.5,1.5) {\small $\times$};
 		\node[c] (x2) at (3.05,1.5) {\small $\times$};
@@
 
-		\draw (0,-1.5) edge[dashed] (h1);	
-		\draw (2.5,-1.5) edge[dashed] (h2);	
-		\draw (8,-1.5) edge[dashed] (hT);	
+		\draw (0,-1.5) edge[dotted] (h1);	
+		\draw (2.5,-1.5) edge[dotted] (h2);	
+		\draw (8,-1.5) edge[dotted] (hT);	
 		\draw (h1.north) edge (x1);
@@
 
-		\draw (-4,4) edge[dashed] (Nx1);
-		\draw (-4,3.25) edge[dashed] (Nx2);
-		\draw (-4,2.5) edge[dashed] (Nx3);
+		\draw (-4,4) edge[dotted] (Nx1);
+		\draw (-4,3.25) edge[dotted] (Nx2);
+		\draw (-4,2.5) edge[dotted] (Nx3);
 
@@
 Given some sequence $[\pmb{h}_1,\dots,\pmb{h}_T]$ (e.g.
-the hidden output of an RNN), we may use an neural function $a$ to obtain a weighting vector $\pmb{a} \in \mathbb{R}^{T}$.
+a full sequence of RNN hidden states), we may use an neural function $a$ to obtain a weighting vector $\pmb{a} \in \mathbb{R}^{T}$.
 Multiplying each sequence element by its corresponding weight and summing up the results, we end up with a context vector $\pmb{c}$.
-Note that when $a$ accepts an external vector (or vector sequence) as its argument, the result is a context-dynamic selection of the $[\pmb{h}_1,\dots]$ sequence.}
+Note that when $a$ accepts an external vector (or vector sequence) as its argument, the result is a context-dynamic selection and linear combination of (parts of) the $[\pmb{h}_1,\dots]$ sequence.}
 \end{figure}
@@
 The output can either represent an approximation for a target vector $\pmb{z}_t \in \mathbb{R}^Y$ (in the supervised learning setting) or encode some action (in the reinforcement learning setting).
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}
+		[auto,
+		scale=0.55,
+		h/.style = {draw=black, rectangle, text centered, text depth=0.5em, text width = 6em, text height=1em,  align=center},
+		c/.style = {draw=black, circle, minimum size=1mm, inner sep=0pt},
+		c2/.style = {draw=black, circle, minimum size=2mm, inner sep=0pt}]
+
+		\node[h, text width=18em] (memory) at (3,0) {Memory};		
+		\foreach \x/\alph/\name in {
+			0/read/{Read Heads},
+			6/write/{Write Head}}
+		{
+			\node[h] (\alph) at (\x, 2.5) {\name};
+		}
+		\node[h] (controller) at (3,5) {Controller};\
+		\node (input) at (0,7.5) {Input};
+		\node (output) at (6,7.5) {Output};
+
+		\draw (-0.3,0.7) edge[->] (-0.3,1.8);
+		\draw (0.3,0.7) edge[<-] (0.3,1.8);
+		\draw (6,0.7) edge[<-] (6,1.8);
+		\draw (-0.3,3.2) edge[->] (2, 4.3);
+		\draw (0.3,3.2) edge[<-] (2.6, 4.3);
+		\draw (6,3.2) edge[<-] (3.6, 4.3);
+
+		\draw (input) edge[->] (controller);
+		\draw (controller) edge[->] (output);
+
+	\end{tikzpicture}
+	\caption[]
+	{\small \textit{}\label{fig:3} High-level view of the DNC.
+The controller receives continuous input from some external source, which is processed and translated to memory reading/writing and computation instructions.
+During its operation, the DNC yields a continuous output stream back to the world.}
+\end{figure}
 \paragraph{Controller}
@@
 \[
-\tag{Next Query Transformation}
+\tag{Next Query}
 \pmb{u}^{k+1} = \pmb{H}\pmb{u}^{k} + \pmb{o}^k 
@@
 The previous sections have presented a summary of the design and functionality of two modern approaches towards enhancing recurrent networks with memory.
-This Section will be devoted to some commentary on what the implications of these networks are, how they compare to one another and what their relevance is to computation as a whole.
+This section will be devoted to some commentary on what the implications of these networks are, how they compare to one another and what their relevance is to computation as a whole.
 
@@
 Examined end-to-end, Differentiable Neural Computers propose a system capable of learning task-specific memory management and computation.
-Its practical use cases may be limited, for the time being, but the contribution it makes as a whole is clear and rather groundbreaker; that of a single, unified machinery capable of learning programs with vastly different functionalities and input/output data structures.
-It is a huge leap towards automated program synthesis and recognition.
-At the same time, the authors pose strong arguments for their design decisions and draw parallels between biological intelligence and their system.
+Its practical use cases may be limited for the time being, but the contribution it makes as a whole is clear and rather groundbreaking; that of a single, unified machinery capable of learning programs with vastly different functionalities and input/output data structures; a great leap towards automated program inference.
+At the same time, the authors pose strong arguments for their design decisions and draw a few interesting parallels between biological intelligence and their system.
 
-Differentiable Neural Computers are the direct successor to Neural Turing Machines\cite{DBLP:journals/corr/GravesWD14}, a related architecture that has the same operative goals but slightly limited functions.
-More specifically, Neural Turing Machines lack the ability to perform temporal linking and dynamic memory allocation, both of which the Differential Neural Computers excel at.
-This in turn disabled them from performing iterative memory retrieval of sequences stored in remote blocks, and hindered their computational capacities at situations when reiterating through a previously used memory matrix.
+Differentiable Neural Computers are the direct successor to Neural Turing Machines\cite{DBLP:journals/corr/GravesWD14}, a related architecture that has the same operative goals but slightly more limited functions.
+More specifically, Neural Turing Machines lack the ability to perform temporal linking and dynamic memory allocation.
+This limitation, in turn, disallows them from performing iterative memory retrieval of sequences stored in disparate blocks, and hinders their computational capacities when attempting to reiterate through a previously used memory matrix.
+Differentiable Neural Computers take specific measures against these problems, as described earlier, and thus excel at both memory allocation and arbitrary sequence retrieval.
+
+End-to-End Memory Networks, on the other hand, make for a more grounded, applied approach.
+The proposal is far less convoluted and more compact in size, but its scope is also less ambitious.
+The overall focus seems to be on question answering tasks, even though the network is proposed as a general use architecture.
+Unlike Differentiable Neural Computers, no measures are taken towards program-centric capabilities; instead, a simple yet efficient mechanism of external memory attention is the paper's sole contribution.
+The exact implementation of this mechanism is clear and easy to follow, but feels somewhat arbitrary at times.
+For instance, no motivation is provided for the particular choices of transformations applied, both in terms of the concrete operations used, as well as their overall necessity.
+
+End-to-End Networks also draw inspiration from a predecessor paper, namely Memory Networks\cite{DBLP:journals/corr/WestonCB14}, which proposed a very similar architecture.
+Despite their similarity, End-to-End Networks make a very important contribution over the original paper.
+Whereas Memory Networks suffer from discontinuities and non-differentiable operations, requiring many levels of human supervision to train, End-to-End Networks resolve these issues by smart application of soft attention.
+Overall, the idea is easy to replicate and employ, serving as a portable and directly usable alternative to standard choices of sequence processing architectures such as the LSTM, at least for tasks requiring query matching and long-term data dependencies.
+
+\subsection{Computational Relevance}
+On another level, neither of the two papers address computation-theoretic problems.
+They are both very technical in nature, and their orientation is that of an engineering perspective.
+This does not, by any means, imply a weakness on their part.
+Neural Networks, and RNNs in particular, are already well-established as powerful machinery for function approximation\cite{Cybenko1989} and are known to be Turing complete\cite{SIEGELMANN1995132}.
+Improvements over their efficiency, training speed and applicability are nontheless extremely important scientific advancements, and as such both papers do progress the fields of both Artificial Intelligence and Computer Science.
 
@@
 \label{Conc}
+Machine learning has been called, often justifiably, an ad-hoc field, riddled with impulsive design decisions.
+Enhancing recurrent networks with memory capacities via attentive interfaces is a grounded, logical approach that seeks to shatter this perception.
+It is a far-reaching idea, deeply rooted in both modern computer science and neurological perspectives of biological intelligence.
+As such, I believe both of the papers presented are quite significant, as they pave the way for exciting new research and applications of neural computation.
+
+In conclusion, fitting two lengthy technical papers into a brief overview is by no means an easy task.
+Several details had to be omitted, and some concessions had to be made on the amount of explanatory background provided.
+Nevertheless, I hope that this paper, as supplemented by the accompanying presentation, has managed to intrigue the interested reader and presented a motivating case towards further researching the topic.
 

### 2018-06-16 Paper/Paper.tex
update based on comments

@@
 Neural networks have been setting new benchmarks in tasks from a broad range of fields, including computer vision, natural language processing and pattern recognition; many of these tasks previously unsolved, and some of these benchmarks surpassing human-level performance.
-Until recently, this astounding potential has for the most part been limited to tasks involving sensory processing and representation learning.
+Until recently, this astounding potential has been, for the most part, limited to tasks involving sensory processing and representation learning.
 Memory-centric tasks, i.e.
@@
 This paper serves as a literature review of two recent approaches towards bypassing this limitation, namely Differentiable Neural Computers\cite{Graves2016} and End-to-End Memory Networks\cite{NIPS2015_5846}.
-The rest of this section will briefly introduce some important background concepts, before some notation is established in Section \ref{sec:Notation}.
+The rest of this section briefly introduces some important background concepts, before some notation is established in Section \ref{sec:Notation}.
 The models' details are examined in Sections \ref{DNC} and \ref{E2E}, respectively.
@@
 This elegant addition accounts for a drastic improvement in the representational capacity of the network.
-Whereas a simple net acts as a trainable (but parametrically fixed) function, a RNN acts as a continuous program operating on sequences of inputs, and is in fact Turing complete\cite{Siegelmann545}.
+Whereas a feedforward net acts as a trainable (but parametrically fixed) function, a RNN acts as a continuous program operating on sequences of inputs, and is in fact Turing complete\cite{Siegelmann545}.
 Under this viewpoint, the RNN's hidden representation can be perceived as the program's internal variables, updating as new inputs are received and affecting the computation as it progresses.
@@
 The first relates to the statefulness achieved by their intermediate representation; even though it is distributed (hence more expressive than stochastic FSAs or Markov models)\cite[Lecture~10]{Hinton13}, the hidden vector's size is finite and fixed, therefore capable of only limited, lossy storage.
-The second is a more intrinsic one and is not only tied to RNNs but neural networks in general; there is no separation between memory and processing, as each neuron is simultaneously a minimal storage unit and a computational one.
-Although appealing from a biological perspective, this goes against the von Neumann model and the modern programming paradigm.
+The second drawback is a more intrinsic one and is not only tied to RNNs but neural networks in general; there is no separation between memory and processing, as each neuron is simultaneously a minimal storage unit and a computational one.
+Although appealing from a biological perspective, this goes against the von Neumann model and the established programming paradigm.
 
@@
 Since its inception, attention has been a key-concept in many influential publications; the creative liberty it is offering, in terms of new potential operations, has also paved the way for architectures which decouple storage from computation.
-Such architectures, including but not limited to the two presented in this paper, utilize large external matrices and employ attention to perform read and write operations on them.
+Such architectures, including (but not limited to) the two presented in this paper, utilize large external matrices and employ attention to perform read and write operations on them.
 
@@
 	\caption[]
-	{\small \textit{}\label{fig:2} General case of an attentional layer.
+	{\small \textit{\label{fig:2} General case of an attentional layer.
 Given some sequence $[\pmb{h}_1,\dots,\pmb{h}_T]$ (e.g.
@@
 Multiplying each sequence element by its corresponding weight and summing up the results, we end up with a context vector $\pmb{c}$.
-Note that when $a$ accepts an external vector (or vector sequence) as its argument, the result is a context-dynamic selection and linear combination of (parts of) the $[\pmb{h}_1,\dots]$ sequence.}
+Note that when $a$ accepts an external vector (or vector sequence) as its argument, the result is a context-dynamic selection and linear combination of (parts of) the $[\pmb{h}_1,\dots]$ sequence.}}
 \end{figure}
@@
 \subsection{Description}
-Inspired by the von Neumann architecture, DNCs model computation as the interfacing between two units; a RNN controller and an external memory matrix, functioning analogously to the CPU and the RAM, respectively.
+Inspired by the von Neumann architecture, Differentiable Neural Computers (or DNCs in short) model computation as the interfacing between two units; a RNN controller and an external memory matrix, functioning analogously to the CPU and the RAM, respectively.
 The memory matrix can be adressed using soft attention mechanisms, allowing selective reading and writing.
@@
 As the system is already equiped with the necessary tools to simulate traditional computation, i.e.
-adressing mechanisms, information storage and retrieval, logical flows and arithmetic processing, a DNC in training is learning the instructions of a program rather than the parameters of a function, and a trained DNC should be able to mimic the behavior of a traditionally hand-written program.
+adressing mechanisms, information storage and retrieval, logical flows and arithmetic processing, a DNC in training is learning the instructions of a program rather than the parameters of a function.
+A trained DNC should then be able to mimic the behavior of a traditionally hand-written program.
 
@@
 \paragraph{Overview} 
-A differentiable neural computer consists of two main components; a recurrent neural network, called the \textbf{controller network}, and an external \textbf{memory matrix} $M \in \mathbb{R}^{N\times W}$.
+A differentiable neural computer consists of two main components; a neural network, called the \textbf{controller network}, and an external \textbf{memory matrix} $M \in \mathbb{R}^{N\times W}$.
 The matrix contains $N$ memory adresses, each of size $W$, which can be read by the controller through $R$ \textit{read heads}, or written to by one \textit{write head}.
@@
 	\caption[]
-	{\small \textit{}\label{fig:3} High-level view of the DNC.
+	{\small \textit{\label{fig:3} High-level view of the DNC.
 The controller receives continuous input from some external source, which is processed and translated to memory reading/writing and computation instructions.
-During its operation, the DNC yields a continuous output stream back to the world.}
+During its operation, the DNC yields a continuous output stream back to the world.}}
 \end{figure}
@@
 Out of the vectors $(\pmb{\upsilon}_t,\ \pmb{\xi}_t)$ returned by the controller, the first corresponds to the intermediate user-level output.
-Before conveying this to the user, the system is allowed one last peak at the memory.
+Before conveying $\pmb{\upsilon}_t$ to the user, the system is allowed one last peak at the memory.
 This is necessitated by the fact that the read head contents at the final timestep of the computation cannot be used in $\mathcal{N}$, as this would introduce circular dependencies in the architecture's computational graph.
@@
 
-The remainder of this section is dedicated to examining the role of each of these components.
+The remainder of this section is dedicated to examining the role of each of these components, in the context of the network's broader functionalities.
 
@@
 
-Each layer applies the memory and output transformations on $pmb{x}$ with each own embedding matrices $A^k, C^k$.
+Each layer applies the memory and output transformations on $\pmb{x}$ with each own embedding matrices $A^k, C^k$.
 The authors, however, explore a few options of weight-sharing in order to reduce the parameter space.
@@
 The previous sections have presented a summary of the design and functionality of two modern approaches towards enhancing recurrent networks with memory.
-This section will be devoted to some commentary on what the implications of these networks are, how they compare to one another and what their relevance is to computation as a whole.
+This section is devoted to some commentary on what the implications of these networks are, how they compare to one another and what their relevance is to computation in general.
 
@@
 This is one of the very first instantations of a model that falls within the domain of \textit{Probabilistic Programming}\cite{Meijer}, an emerging programming paradigm that proposes treating computer programs as stochastic distributions.
-Examined end-to-end, Differentiable Neural Computers propose a system capable of learning task-specific memory management and computation.
+Examined end-to-end, DNCs propose a system capable of learning task-specific memory management and computation.
 Its practical use cases may be limited for the time being, but the contribution it makes as a whole is clear and rather groundbreaking; that of a single, unified machinery capable of learning programs with vastly different functionalities and input/output data structures; a great leap towards automated program inference.
-At the same time, the authors pose strong arguments for their design decisions and draw a few interesting parallels between biological intelligence and their system.
+At the same time, the authors pose strong arguments for their design decisions and draw a few interesting parallels between biological intelligence and their system
 
-Differentiable Neural Computers are the direct successor to Neural Turing Machines\cite{DBLP:journals/corr/GravesWD14}, a related architecture that has the same operative goals but slightly more limited functions.
+DNCs are the direct successor to Neural Turing Machines\cite{DBLP:journals/corr/GravesWD14}, a related architecture that has the same operative goals but slightly more limited functions.
 More specifically, Neural Turing Machines lack the ability to perform temporal linking and dynamic memory allocation.
 This limitation, in turn, disallows them from performing iterative memory retrieval of sequences stored in disparate blocks, and hinders their computational capacities when attempting to reiterate through a previously used memory matrix.
-Differentiable Neural Computers take specific measures against these problems, as described earlier, and thus excel at both memory allocation and arbitrary sequence retrieval.
+DNCs take specific measures against these problems, as described earlier, and thus excel at both memory allocation and arbitrary sequence retrieval.
 
@@
 
-End-to-End Networks also draw inspiration from a predecessor paper, namely Memory Networks\cite{DBLP:journals/corr/WestonCB14}, which proposed a very similar architecture.
+End-to-End Networks also draw inspiration from a predecessor paper, namely Memory Net-
+works\cite{DBLP:journals/corr/WestonCB14}, which proposed a very similar architecture.
 Despite their similarity, End-to-End Networks make a very important contribution over the original paper.
@@
 
-\subsection{Computational Relevance}
 On another level, neither of the two papers address computation-theoretic problems.
-They are both very technical in nature, and their orientation is that of an engineering perspective.
 This does not, by any means, imply a weakness on their part.
 Neural Networks, and RNNs in particular, are already well-established as powerful machinery for function approximation\cite{Cybenko1989} and are known to be Turing complete\cite{SIEGELMANN1995132}.
-Improvements over their efficiency, training speed and applicability are nontheless extremely important scientific advancements, and as such both papers do progress the fields of both Artificial Intelligence and Computer Science.
+Improvements over their efficiency, training speed and applicability are nontheless extremely important engineering advancements, and as such both papers do progress the fields of both Artificial Intelligence and Computer Science, albeit from an applied standpoint.
 
@@
 It is a far-reaching idea, deeply rooted in both modern computer science and neurological perspectives of biological intelligence.
-As such, I believe both of the papers presented are quite significant, as they pave the way for exciting new research and applications of neural computation.
+Consequently, I believe both of the papers presented are of great significance, as they pave the way for exciting new research and applications of neural computation.
 
-In conclusion, fitting two lengthy technical papers into a brief overview is by no means an easy task.
+To conclude, fitting two lengthy technical papers into a brief overview is by no means an easy task.
 Several details had to be omitted, and some concessions had to be made on the amount of explanatory background provided.
-Nevertheless, I hope that this paper, as supplemented by the accompanying presentation, has managed to intrigue the interested reader and presented a motivating case towards further researching the topic.
+Nevertheless, I hope that this paper, as supplemented by the accompanying presentation, has managed to intrigue the interested reader and presented a motivating case towards further researching the subject.
 

### 2018-06-16 Paper/Paper.tex
fixing notation

@@
 \paragraph{Overview}
-An end-to-end memory network receives two inputs; a sequence of vectors $\{\pmb{x}_1,\dots,\pmb{x}_N\}$ and a query $\pmb{q}$.
+An end-to-end memory network receives two inputs; a sequence of vectors $]\pmb{x}_1,\dots,\pmb{x}_N]$ and a query $\pmb{q}$.
 Both $\pmb{x}_i$ and $\pmb{q}$ are defined as symbols originating from a vocabulary $\mathcal{V}$.
@@
 Given a character $x$ that coincides with the i-th element of $\mathcal{V}$, one-hot encoding is achieved by mapping $x$ to a vector $\pmb{x}$ whose elements are all $0$, except the $i$-th element which is $1$.
-This is the assumed form of input representation for the sequence $\{\pmb{x}_i\}$ and the query $\pmb{q}$.
+This is the assumed form of input representation for the sequence $[\pmb{x}_1,\dots]$ and the query $\pmb{q}$.
 
@@
 It essentially accounts for a form of soft attention; the query dictates which parts of the output representation to focus on, depending on how it matched with the input representation.
-In other words, even though we always get the same output representation sequence $\{\pmb{c}_i\}$ from some input sequence $\{\pmb{x}_i\}$, the query $\pmb{q}$ plays an important role on how the network utilizes it.
+In other words, even though we always get the same output representation sequence $[\pmb{c}_1,\dots]$ from some input sequence $[\pmb{x}_1,\dots]$, the query $\pmb{q}$ plays an important role on how the network utilizes it.
 

### 2018-06-23 Paper/Paper.tex
final

@@
 \usetikzlibrary{calc, trees, fit, positioning}
+\usepackage{bm}
 
@@
 This elegant addition accounts for a drastic improvement in the representational capacity of the network.
-Whereas a feedforward net acts as a trainable (but parametrically fixed) function, a RNN acts as a continuous program operating on sequences of inputs, and is in fact Turing complete\cite{Siegelmann545}.
+Whereas a feedforward net acts as a trainable (but parametrically fixed) function, an RNN acts as a continuous program operating on sequences of inputs, and is in fact Turing complete\cite{Siegelmann545}.
 Under this viewpoint, the RNN's hidden representation can be perceived as the program's internal variables, updating as new inputs are received and affecting the computation as it progresses.
@@
 	\caption[]
-	{\small \textit{Comparison between a feedforward neural network and a RNN.
+	{\small \textit{Comparison between a feedforward neural network and an RNN.
 (a) The simple network applies two transformations $\pmb{x} \mapsto \pmb{h}$ and $\pmb{h} \mapsto \pmb{y}$, the composition of which can be seen as a function $\pmb{x} \mapsto \pmb{y}$.
@@
 A series of advancements has seeked to enhance RNNs with stronger memory management.
-Starting with the introduction of the \textit{Long Short-Term Memory}\cite{Hochreiter:1997:LSM:1246443.1246450,Gers99learningto}, which permits finite storage over very long computations, research in RNNs has bloomed towards many different directions.
+Starting with the introduction of the \textit{Long Short-Term Memory} (LSTM)\cite{Hochreiter:1997:LSM:1246443.1246450,Gers99learningto}, which permits finite storage over very long computations, research in RNNs has bloomed towards many different directions.
 One particularly exciting recent advancement is the so-called \textit{attentional interface}\cite{NIPS2014_5542,Bahdanau} (Fig.\ref{fig:2}), which allows a network to selectively shift its focus on particular indices over a set of dimensions of an arbitrary tensor, thus enabling content-based adressing.
@@
 Given some sequence $[\pmb{h}_1,\dots,\pmb{h}_T]$ (e.g.
-a full sequence of RNN hidden states), we may use an neural function $a$ to obtain a weighting vector $\pmb{a} \in \mathbb{R}^{T}$.
+a full sequence of RNN hidden states), we may use a neural function $a$ to obtain a weighting vector $\pmb{a} \in \mathbb{R}^{T}$.
 Multiplying each sequence element by its corresponding weight and summing up the results, we end up with a context vector $\pmb{c}$.
@@
 \subsection{Description}
-Inspired by the von Neumann architecture, Differentiable Neural Computers (or DNCs in short) model computation as the interfacing between two units; a RNN controller and an external memory matrix, functioning analogously to the CPU and the RAM, respectively.
+Inspired by the von Neumann architecture, Differentiable Neural Computers (or DNCs in short) model computation as the interfacing between two units; a neural controller and an external memory matrix, functioning analogously to the CPU and the RAM, respectively.
 The memory matrix can be adressed using soft attention mechanisms, allowing selective reading and writing.
 As both the controller and the interfacing are differentiable, the full architecture is end-to-end differentiable, essentially allowing it to be trained purely with data and minimal human supervision.
-As the system is already equiped with the necessary tools to simulate traditional computation, i.e.
+Since the system is already equiped with the necessary tools to simulate traditional computation, i.e.
 adressing mechanisms, information storage and retrieval, logical flows and arithmetic processing, a DNC in training is learning the instructions of a program rather than the parameters of a function.
@@
 Contrary to first impressions, the above equation is quite intuitive.
-The parenthesized term sums the previous usage tracking vector with the current write weighting minus their dot product, acting as a real-valued variation of the logical OR function.
+The parenthesized term sums the previous usage tracking vector with the current write weighting minus their dot product, acting as a real-valued variation of the logical disjunction function.
 A single element of this term, $\pmb{u}_t[i]$ would denote the pre-retention usage tracking of memory address $i$; it is close to $1$ if it was either already in use, or just written to.
@@
 Temporal linking is necessary in order to perform sequential retrieval, when sequences are stored in disparate, non-contiguous blocks.
-The key-element of the process is a temporal transition matrix $\pmb{L} \in [0,1]^{N\times N}$, which keeps track of the temporal order by which memory addresses have been written to.
+The key-element of the process is a \textit{temporal transition matrix} $\pmb{L} \in [0,1]^{N\times N}$, which keeps track of the temporal order by which memory addresses have been written to.
 More conretely, $\pmb{L}[i,j]$ is close to $1$ if $j$ was strongly written to after $i$, or close to $0$ otherwise.
@@
 The first term of the addition allows the transition value between $i$ and $j$ to propagate through time.
-The extend of propagation of the old transition, $\pmb{L}_{t-1}[i,j]$, is complentary to the amount of writing performed in these addresses; even if we had a transition in the past, it no longer holds if either $i$ or $j$ were just written to.
+The extend of propagation of the old transition, $\pmb{L}_{t-1}[i,j]$, is complentary to the amount of writing performed in these addresses; even if a transition from $i$ to $j$ had taken place in some past step, it no longer holds if either $i$ or $j$ were just written to.
 On the other hand, if $i$ was written to in the previous timestep and $j$ was written to in the current timestep, then a new transition is instantiated.
@@
 \subsection{Description}
-An end-to-end memory network is a neural architecture that also connects a RNN with a large memory array.
+An end-to-end memory network is another neural architecture that connects an RNN with a large memory array.
 The external nature of this array is disanalogous to traditional architectures, such as the LSTM, where the memory is encapsulated within the neural layers.
@@
 \paragraph{Overview}
-An end-to-end memory network receives two inputs; a sequence of vectors $]\pmb{x}_1,\dots,\pmb{x}_N]$ and a query $\pmb{q}$.
-Both $\pmb{x}_i$ and $\pmb{q}$ are defined as symbols originating from a vocabulary $\mathcal{V}$.
+An end-to-end memory network receives two inputs; a sequence of vectors $[\pmb{x}_1,\dots,\pmb{x}_N]$ and a query $\pmb{q}$.
+Both $\pmb{x}_i$ and $\pmb{q}$ are consist of symbols originating from a vocabulary $\mathcal{V}$.
 The network processes these inputs to return an answer $\pmb{a}$.
@@
 The authors treat two different cases of this process; the first and simplest one employing a single layer, and the second, more general one, employing multiple layers.
-As this approach is favorable for understanding the architecture, we are also going to follow along the same route, modulo a few minor alterations and clarifications.
+As this approach is favorable for understanding the architecture, this section follows along the same route, modulo a few minor alterations and clarifications.
 
@@
 
-As soon as we obtain the above, the matching vector $\pmb{p}$ between the query transformation and each memory object can be computed by passing the product of the two, $\pmb{u}^\top \pmb{m}_i$, through a Softmax activation:
+As soon as we obtain the above, the matching vector $\pmb{p}$ between the query transformation and each memory object can be computed by passing the product of the two, $\pmb{u}^\top \pmb{m}_i$, through a softmax activation:
 \[
@@
 
-A third transformation, via a third embedding matrix $\pmb{C} \in \mathbb{R}^{d\times V}$, is used to map inputs $\{\pmb{x}_i\}$ to their output representations $\{\pmb{c}_i\}$, from which the memory response can be derived as their match-weighted sum:
+A third transformation, via an embedding matrix $\pmb{C} \in \mathbb{R}^{d\times V}$, is used to map inputs $\pmb{x}_i$ to their output representations $\pmb{c}_i$, from which the memory response can be derived as their match-weighted sum:
 \begin{align}
@@
 concatenation, element-wise addition or multiplication, etc.) and is passed through one last layer responsible for the final prediction.
-In the original paper, which assumes a classification setting, the authors propose a Softmax-activated linear map over the addition of the query and the response:
+In the original paper, which assumes a classification setting, the authors propose a softmax-activated linear map over the addition of the query and the response:
 \[
